\chapter{Preface}
\rule{\textwidth}{0.5pt}    % Line 
\thispagestyle{fancy}

This project is a personal undertaking to rewrite and annotate the Holy Bible for study, reflection, and understanding. The primary text used throughout is the \textit{New King James Version (NKJV)}, though other translations may occasionally be referenced where clarity, variation, or historical interest requires. Each book of the Bible is treated as a separate chapter, and each begins with a brief summary outlining its themes or narrative structure.

\tab The scripture is presented verse by verse using a custom format that allows for inline references and annotations. These annotations include (but are not limited to) historical background, translation notes, literary and cultural context, scientific references, theological or reflective questions, and general comments. Each of these various types are also color-coded for ease of reference/reading. They are marked inline with a custom symbol (e.g., \vmark{$\star$}) and collected directly below the verse for easy association.

\tab This is an ongoing and evolving project. At the time of writing this preface, it is highly incomplete and is being developed incrementally. As updates, corrections, and expansions are made, the version number of the document will be incremented accordingly. This allows for tracking progress and identifying updated material across future iterations. This work is intended for personal study and is freely shareable for non-commercial purposes.

\rule{\textwidth}{0.5pt}    % Line 


\subsection*{Various Subtle Formatting Meanings}

There are various subtle formatting techniques which have specific meanings, These are outlined below:
\begin{itemize}
	\item As done in the NKJV, scriptural words which are \textit{italicized} are `added', but are not meant to change any meaning - only to provide better understanding with our modern English language. Within the commentary and notes, \textit{italics} are instead used as they typically are in standard English writings - for emphesis or proper reference formatting.
	\item Scripture numbers are in \textbf{bold} for ease of finding.
	\item Words that Jesus spoke are \jesus{quoted and in red.}
\end{itemize}




\subsection*{Note Types and Symbols}

The following is a list of annotation types used throughout this work. Each note is marked with a specific icon and color to indicate its category and purpose:\medskip

\historicalnote{History}{Provides historical or cultural background relevant to the verse or passage, such as ancient customs, geopolitical context, or historical events.}\medskip

\translationnote{Translation}{Offers insight into the original language, alternative translations, or meanings of words and phrases from the Hebrew, Aramaic, or Greek texts.}\medskip

\contextnote{Context}{Highlights the literary, narrative, or cultural context of a passage, aiding in its interpretation and situational relevance.}\medskip

\sciencenote{Science}{Connects the passage to scientific ideas, natural phenomena, or the relationship between scriptural content and modern science.}\medskip

\questionnote{Question}{Poses theological, philosophical, or reflective questions raised by the verse, encouraging deeper thought and study.}\medskip

\sermonnote{Sermon}{Presents insights, illustrations, or applications drawn from sermons. These notes may include quotes, thematic connections, or interpretations offered by preachers, providing a homiletic perspective that complements the text.}\medskip

\crossrefnote{Cross-reference}{Identifies connections to other passages of Scripture, highlighting thematic, prophetic, or textual parallels that provide interpretive insight or support broader biblical understanding.}\medskip

\geographynote{Geography}{Provides geographical information related to the passage, such as locations, travel routes, terrain features, and regional significance. This can aid in contextualizing the narrative within its physical setting.}\medskip

\doctrinenote{Doctrine}{Highlights theological principles, doctrines, or key insights derived from the passage. These notes may address topics such as the nature of God, salvation, sin, covenant, or other foundational beliefs, helping readers engage with the text theologically.}\medskip

\literarynote{Literary}{Draws attention to the literary qualities of the text, such as poetic structure, metaphor, genre, parallelism, or symbolic language. These notes help identify stylistic features that shape interpretation and highlight the artistry of the biblical text.}\medskip

\philosophicalnote{Philosophy}{Engages with metaphysical, existential, or interpretive ideas raised by the passage. These notes may reflect on questions of meaning, purpose, reality, or the nature of existence from a philosophical or worldview-oriented perspective. While not strictly theological or doctrinal, they aim to deepen reflection by considering how the text interfaces with broader human inquiry.}

\generalnote{Note}{A general-purpose note for observations, clarifications, or commentary that doesn't fall into one of the above categories.}\medskip





\subsection*{Referencing and Sources}

Throughout this work, I include notes and annotations drawn from a variety of sources. Where references are uncommon, specialized, or potentially unfamiliar, I have made an effort to cite them directly in the notes. However, extremely common reference materials, such as general-use dictionaries, Wikipedia, or widely known facts, are not individually cited. My goal is to maintain clarity without overburdening the text with unnecessary attributions, while still giving appropriate credit where due.

\tab Given the potential volume of references involved, not every source will be perfectly accurate. However, the aim is to identify and cross-check sources that corroborate one another to improve reliability. I consistently strive to reference high-quality material and present information that reflects careful consideration and verification. That said, with certain subjects, such as Hebrew translation nuances, this level of validation is not always possible or straightforward, and in such cases I will primarily rely on the work and interpretation of external sources.




\subsection*{Important Disclaimer}

Because I am manually typing and writing each scripture by hand - there is a very large chance for human error. Although I will try to remain diligent and record all scriptures accurately, at times, typos and potentially even missed lines may be missed. This is simply the fallibility of being human. This is entirely unintentional and will be fixed and corrected as any mistakes are found or pointed out. If you (as a reader) finds any of these, please bring them to the attention of the author.
