\documentclass[10pt]{article}

%%% These are some packages that are useful
\usepackage{amsmath,amssymb, amscd,amsbsy, amsthm, enumerate}
\usepackage[export]{adjustbox}
\usepackage{lastpage}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[unicode]{hyperref}
\usepackage{tikz, pgfplots, xcolor, fancyhdr}
\usepackage{multicol}
\usepackage{lipsum}

%%% Page formatting
%\setlength{\headsep}{30pt}
\setlength{\textheight}{9in}
\newcommand{\tab}{\hspace{1cm}}
%\setlength{\parindent}{25pt}

\title{A Lion In A Cage}
\author{Antonius Torode}

%%% Header and Footer Info
\pagestyle{fancy}
\fancyhead[L]{{\large Template - \textbf{Change 03}}}
\fancyhead[C]{\today}
\fancyhead[R]{Name: Antonius Torode}


\fancyhf{} % sets both header and footer to nothing
\renewcommand{\headrulewidth}{0pt}
% your new footer definitions here

\fancyfoot[L]{}
\fancyfoot[C]{}
\fancyfoot[R]{\thepage\ of \pageref{LastPage}}

% Used to define spacing and format of References
\let\OLDthebibliography\thebibliography
\renewcommand\thebibliography[1]{
	\OLDthebibliography{#1}
	\setlength{\parskip}{0pt}
	\setlength{\itemsep}{0pt plus 0.3ex}
}

%%% Document Starts now
\begin{document}

\maketitle
\thispagestyle{fancy}

\begin{multicols}{2}

Imagine you are a lion, living out in the wild pastures. When you're hungry, you hunt some of the local prey. You've never died of hunger - there's food to hunt for all over. When you're tired, you lay under the vast stars of the heavens. You can wander to and fro, far and wide, seeing the beautiful sights that nature has to offer. When you're ready to relax, you have the sounds of the birds chirping around you, the streams and waterfalls flowing around. Life is good... right?

One day a pack of hyenas comes around and starts bothering you. When you turn your back, they steal the food you hunted for. If you fall asleep, they may even try to eat \textit{you}. You begin to realize it's not as safe as you thought. One day, the sun burns bright. The heat makes you tired and weak as the sun burns on your skin. Another day, rain comes and stays for days on end. Your pelt stays wet and refuses to dry. You realize that you don't quite have the shelter you need. One day you don't manage to catch the prey you chased. You're tired and weak, you haven't eaten in days. You begin to realize that hunger is not a very fun feeling. If only you had some food, life would be good again. You then see a porcupine. As hungry as you are, you go after it, only to come away with a paw full of needles. The needles are sharp and piercing - a constant stinging. If only you had a doctor, life would be good.

Along comes a man. He looks at the struggles you have and makes you an offer which sounds too good to be true. ``Little lion, how would you like free food? I can feed you promptly each day. How would you like free shelter? I can give you a solid roof over your head. How would you like free security? I can keep all of the hyenas from pestering you. How would you like free healthcare? I can take care of your paws every time you step on a spike. All this for you, for free'' You may wonder what the catch is, but there's no catch - he's offering exactly what he says he is. Of course, you accept the offer! With all these things, life will be great!

And so sure enough, everyday you are handed free food. The hyenas no longer sneak around when you're not looking. The sun no longer burns on your skin and the rain no longer keeps you wet for days. You realize now that life will be truly good - better than ever before.

After a short period of time, you begin to tire of the same meal each day. You miss the thrill of the hunt. You miss the freshness of the food. You realize that your legs are weakening as you no longer wander to and fro. All you do now is lay around. You begin to miss the relaxing peace of sitting in the rain or bathing in the sun. One day you roll over and lay on your back to relax, only to realize... the stars are gone. The birds no longer chirp. The fountains no longer flow in the distance. You look around and wonder, where are you? You realize that you are now living in a cage.



\begin{thebibliography}{9}
	{\footnotesize
	\bibitem{tmp} tmp

	}
\end{thebibliography}

\end{multicols}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}





















