\documentclass[10pt]{article}

%%% These are some packages that are useful
\usepackage{amsmath,amssymb, amscd,amsbsy, amsthm, enumerate}
\usepackage[export]{adjustbox}
\usepackage{lastpage}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[unicode]{hyperref}
\usepackage{tikz, pgfplots, xcolor, fancyhdr}
\usepackage{multicol,caption}
\usepackage{lipsum}
\usepackage[version=4]{mhchem}
\usepackage{float}
\usepackage{enumitem}

%%% Page formatting
%\setlength{\headsep}{30pt}
\setlength{\textheight}{9in}
\newcommand{\tab}{\hspace{1cm}}
%\setlength{\parindent}{25pt}

\title{Know Thy Enemy (Part 4) 	: Baal}
\author{Antonius Torode}

%%% Header and Footer Info
\pagestyle{fancy}
\fancyhead[L]{{\large Template - \textbf{Change 03}}}
\fancyhead[C]{\today}
\fancyhead[R]{Name: Antonius Torode}


\fancyhf{} % sets both header and footer to nothing
\renewcommand{\headrulewidth}{0pt}
% your new footer definitions here

\fancyfoot[L]{}
\fancyfoot[C]{}
\fancyfoot[R]{\thepage\ of \pageref{LastPage}}

% Used to define spacing and format of References
\let\OLDthebibliography\thebibliography
\renewcommand\thebibliography[1]{
	\OLDthebibliography{#1}
	\setlength{\parskip}{0pt}
	\setlength{\itemsep}{0pt plus 0.3ex}
}

\newenvironment{Figure}
  {\par\medskip\noindent\minipage{\linewidth}}
  {\endminipage\par\medskip}


%%% Document Starts now
\begin{document}

\maketitle
\thispagestyle{fancy}


%\begin{abstract}
%TODO
%\end{abstract}

\begin{multicols}{2}

In the previous part of this series, I demonstrated that the old gods are still around and active in today's age - as they have been throughout history \cite{part3}. One of the most known and most mentioned of the old gods is Baal. Throughout scripture, Baal appears as the head deity of the Canaanites and Phoenicians and tied to agriculture, storms and rain, fertility, child sacrifice\footnote{Jeremiah 19:5 - ``And have built the high places of Baal to burn their sons in the fire as burnt offerings to Baal.''}, and political power\footnote{There is a constant theme in the scriptures of entire nations bending to and worshiping Baal. An example being Judges 2:11-13 - ``Then the children of Israel did evil in the sight of the Lord, and served the Baals'' ... ``They forsook the Lord and served Baal and the Ashtoreths.''}\cite{baal strongs}. Baal is referenced about 80 times in the old testament alone. The context is almost always that of spiritual adultery and apostasy \footnote{``An act of refusing to continue to follow, obey, or recognize a religious faith'' \cite{apostasy defn}}\cite{baal strongs}.
This framing of Baal is from ancient times; therefore, what is Baal's role in the modern age?

The Hebrew word \textit{Baal} literally means `lord' \cite{Strong's GodRules}, `master'\cite{baal strongs}, or 'owner`\cite{baal strongs}.
The meaning of his name essentially summarizes his role. His signature routine is that he becomes the \textit{lord} of a nation by \textit{replacing} God in the eyes of the people. That pattern is evident by the scriptures and myths of how Baal works. However, surprisingly, there is not much information about who or what Baal is. The scriptures certainly don't explain it - despite the mention of Baal numerous times. The idea and concept of Baal is nearly always assumed to be known and understood by the reader. When you research Baal, you find very few details. The details that are found are in the form of ancient myths, stories, and recurring patterns that have unfolded in the aftermath of his works. 

Baal often appears throughout cultures with different names - such as Baal Peor\footnote{Deuteronomy 4:3 - ``Your eyes have seen what the LORD did at Baal Peor; for the LORD your God has destroyed from among you all the men who followed Baal of Peor.''}, Baal-Zebub\footnote{2 Kings 1:16 - ``Then he said to him, ``Thus says the LORD: ‘Because you have sent messengers to inquire of Baal-Zebub, the god of Ekron, is it because there is no God in Israel to inquire of His word? ...''}, Baal-Berith\footnote{Judges 8:33 - ``So it was, as soon as Gideon was dead, that the children of Israel again played the harlot with the Baals, and made Baal-Berith their god.''}, and many more. He is both spoken of as one and many. This makes Baal seem almost more of a \textit{concept} rather than the surname of a single \textit{entity}. That concept would simply be that of apostasy - opposing God. There are even some less-accepted lines of thought that suggest Baal could even be Satan himself - suggesting that versions of his name, \textit{Beelzebul} are simply distortions of \textit{Beelzebub} - the king of the demons \cite{Yahweh and gods}. Regardless, he is a being who is clearly in \textit{opposition} of God - a sort of anti-God.

One of the oldest set of texts we (humans) have discovered are the Ugaritic letters and ritual texts. These texts were discovered in 1929 in modern-day Syria. These texts were written in a mix of Akkadian scripts and Semitic languages and identified to be from around the time of 1400-1200 B.C \cite{Ugaritic Letters}. These texts, if you take them at their word, reveal that Baal is actually the epithet of a single cosmic deity - despite having local, personal names for various nations. Each of those various names represent different manifestations of the same being. These texts suggest that the Canaanites actually began equating 'Yahweh and Baal' as the same being. They convinced themselves that Baal \textit{was} Yahweh. They saw Baal as their giver of grains, wine, and oil - which placed him as the leader of their nation. They baked that concept into their daily lives, their language, and even their names \cite{Yahweh and gods}. This is a large part of the context for the book of Hosea. The conflation of Yahwen and Baal was what Hosea was countering:

\begin{quotation}
``For she did not know That \textit{I} gave her grain, new wine, and oil, And multiplied her silver and gold--\textit{Which they prepared for Baal}.'' - Hosea 2:8
\end{quotation}

This is the scheme of Baal.  


\begin{thebibliography}{9}
{\footnotesize
	
	\bibitem{part3} Torode, Antonius, \textit{Know Thy Enemy (part 3): The Old Gods}, June 2026.  \url{https://github.com/torodean/bible-notes/blob/main/sermonettes/Know%20Thy%20Enemy/The%20Old%20Gods/The%20Old%20Gods.pdf}
	
	\bibitem{baal strongs} Bible Hub: Baal. Accessed 27 June 2026. \url{https://biblehub.com/hebrew/1167.htm}, \url{https://biblehub.com/hebrew/1168.htm}
	
	\bibitem{apostasy defn} “Apostasy.” Merriam-Webster.com Dictionary, Merriam-Webster, https://www.merriam-webster.com/dictionary/apostasy. Accessed 27 June 2026.
	
	\bibitem{Strong's GodRules} ``KJV W/ STRONGS BIBLE.'' \url{https://godrules.net/library/kjvstrongs/kjvstrongs.htm}
	
	\bibitem{Yahweh and gods} John Day, \textit{Yahweh and the gods and goddesses of Canaan}, Journal for the study of the old testament supplement series 265. Book
		
	\bibitem{Ugaritic Letters} Dennis Pardee, \textit{Ugaritic Letters and Ancient Texts}, University of Chicago, Accessed 11 Jul 2026. \url{https://isac.uchicago.edu/sites/default/files/uploads/shared/docs/ar/81-90/82-83/82-83_Ugaritic.pdf}

}
\end{thebibliography}

\end{multicols}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}





















}{den}