\documentclass[10pt]{article}

%%% These are some packages that are useful
\usepackage{amsmath,amssymb, amscd,amsbsy, amsthm, enumerate}
\usepackage[export]{adjustbox}
\usepackage{lastpage}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[unicode]{hyperref}
\usepackage{tikz, pgfplots, xcolor, fancyhdr}
\usepackage{multicol,caption}
\usepackage{lipsum}
\usepackage[version=4]{mhchem}
\usepackage{float}
\usepackage{enumitem}

%%% Page formatting
%\setlength{\headsep}{30pt}
\setlength{\textheight}{9in}
\newcommand{\tab}{\hspace{1cm}}
%\setlength{\parindent}{25pt}

\title{Know Thy Enemy: One World Order (Part 2)}
\author{Antonius Torode}

%%% Header and Footer Info
\pagestyle{fancy}
\fancyhead[L]{{\large Template - \textbf{Change 03}}}
\fancyhead[C]{\today}
\fancyhead[R]{Name: Antonius Torode}


\fancyhf{} % sets both header and footer to nothing
\renewcommand{\headrulewidth}{0pt}
% your new footer definitions here

\fancyfoot[L]{}
\fancyfoot[C]{}
\fancyfoot[R]{\thepage\ of \pageref{LastPage}}

% Used to define spacing and format of References
\let\OLDthebibliography\thebibliography
\renewcommand\thebibliography[1]{
	\OLDthebibliography{#1}
	\setlength{\parskip}{0pt}
	\setlength{\itemsep}{0pt plus 0.3ex}
}

\newenvironment{Figure}
  {\par\medskip\noindent\minipage{\linewidth}}
  {\endminipage\par\medskip}


%%% Document Starts now
\begin{document}

\maketitle
\thispagestyle{fancy}


%\begin{abstract}
%TODO
%\end{abstract}

\begin{multicols}{2}

A classic and well known `conspiracy theory` is that society is leading down a path which will inevitably lead to a \textit{one world government}. Other names for this may be a \textit{New World Order}, \textit{Global State}, \textit{Beast Power}, or more. Any bible scholar knows that this is not a `conspiracy', but rather something prophesied in Revelation - where the entire world will be under a single Beast Power which has authority over every tribe, tongue, and nation\footnote{Revelation 13:7 - ``It was granted to him to make war with the saints and to overcome them. And authority was given him over every tribe, tongue, and nation.''}. The Bible teaches that there will be a time where everyone, both small and great, rich and poor, free and slave will not be able to buy or sell without a \textit{mark} of the beast power\footnote{Revelation 13:16-17 - ``He causes all, both small and great, rich and poor, free and slave, to receive a mark on their right hand or on their foreheads, and that no one may buy or sell except one who has the mark or the name of the beast, or the number of his name.''}. This is a concept that was discussed often back during the days of the \textit{World Wide Church of God}\footnote{The immediate audience for this message is the \textit{United Church of God} (UCG), which was a continuation of the original beliefs of the \textit{World Wide Church of God} from the previous century. Most of the audience in UCG would be aware of this.}, but is not a topic I've heard discussed or talked about in recent times. Perhaps it's because most of us are well aware of this - but one thing I've never heard explored is the \textit{why}. \textit{Why} would Satan want a One World Government? \textit{Why} would he push society towards a Beast Power?

Obviously, as humans, we cannot fully know the mind or motives of God, Satan, or any other being (angels, demons, or even other people). However, we can often understand \textit{plausible} reasons behind actions to make sense of them. This is one way of understanding the \textit{why} behind actions and a way of understanding why Satan would want a One World System. Simply put, a One World System is a counterfeit to Divine Sovereignty - it will transform Satan to `be like God.' One of Satan's ultimate goals is to \textit{be like the Most High}.

\begin{quotation}
For you have said in your heart:
`I will ascend into heaven,
I will exalt my throne above the stars of God;
I will also sit on the mount of the congregation
On the farthest sides of the north;
I will ascend above the heights of the clouds,
\textit{I will be like the Most High}.' - Isaiah 14:13-14
\end{quotation}

How does one \textit{be like God}? Satan does not want to become God in just any ordinary sense. This is the desire to \textit{exalt his throne} above God's - to match and surpass His power and authority. This is no easy task. Take one small feature of God - His omnipresence for example. 

\begin{quotation}
``Am I a God near at hand,'' says the Lord,
``And not a God afar off?
Can anyone hide himself in secret places,
So I shall not see him?'' says the Lord;
``Do I not fill heaven and earth?'' says the Lord. - Jeremiah 23:23-24
\end{quotation}

God is clearly omnipresent, but is the Devil also omnipresent? No. There are numerous scriptures which support this. First, he is spoken of as wandering the earth - walking to and fro. 

\begin{quotation}
And the Lord said to Satan, ``From where do you come?'' So Satan answered the Lord and said, ``From going to and fro on the earth, and from walking back and forth on it.'' - Job 1:7\footnote{And Job 2:2}
\end{quotation}

He is never discussed as being in multiple places at once. It is always a localized place. Second, he is mentioned as both entering and departing individuals\footnote{Luke 22:3 - ``Then Satan entered Judas, surnamed Iscariot, who was numbered among the twelve.''} - again implying localized actions. And lastly, we know there are actions we can take to make him flee from us\footnote{James 4:7 - ``Therefore submit to God. Resist the devil and he will flee from you.''}, just as he left Jesus after trying to tempt him in the wilderness\footnote{Matthew 4:11 - ``Then the devil left Him, and behold, angels came and ministered to Him.''}. It should therefore be clear that omnipresence is \textit{not} a trait that Satan has. However, in order to \textit{be like the Most High}, it is a \textit{necessary} one. Given this, how does an entity \textit{become} omnipresent? 

If this was your goal, you would put a microphone in every hand. A camera in every hand. A camera at every intersection, in every car, on every personal computer, at every front door, in every bedroom. You would want every device to be smart, capable of listening - a microphone in every fridge, television, watch, speaker, thermostat. You would want a microphone in anything and everything. You would catalog every person: DNA, fingerprints, biometrics. You would keep a file for each one and tie authentication to biometrics, giving you constant location data. You would watch every corner of the Earth. Every ocean, continent, and border. Did you know Planet Labs collects over 300 million square kilometers of high resolution satellite imagery every single day \cite{PlanetLabs}. That's over twice the entire land-mass of earth - daily. All of this information would flow into a sophisticated analytical system. An artificial intelligence capable of processing it all...

But all of these things aren't enough. No amount of data alone can grant power. No amount of surveillance alone can grant control. None of these things mentioned actually help towards a goal of omnipotence until you introduce one more factor - a beast power. A single global government, with central control. These systems just existing is not enough - omnipresence requires total control. Is that why Satan would want a one world government?

What if I told you that observations alone isn't even the real power here? What I've mentioned so far is only the beginning. Once you control enough data, the possibilities change drastically. Once a system sees everything, it then begins to predict everything. 

Companies today already use their data for behavioral targeting. AI is getting so advanced that it can `predict buyer intent with astonishing accuracy' - essentially reading the minds of the masses. Advertisements are already tailored specifically based on your personal data:
\begin{itemize}[noitemsep, topsep=0pt]
	\item What did you like? 
	\item Where did you click?
	\item How long did you hover?
\end{itemize}
Have you ever said something aloud and within minutes seen an advertisement for it? What about just thinking something? If you haven't experienced it, that already happens today.

With all of these capabilities under your control, you would not only have the ability to be \textit{everywhere}, but also to predict everything, and even to nudge and influence all that is around you. You could convince every person, both small and great, rich and poor, free and slave, to receive your mark and submit to your will. This is bordering more than just omnipresence, but omniscience. All it requires is a simple little beast power - a one world government, along with all the tools we already have today.

Of course, this is not real omniscience (or even omnipresence for that matter). But rather, it's a counterfeit to Divine Sovereignty. Satan can never be \textit{like the Most High}. He will try. God, on the other-hand, is omniscient. A counterfeit is never as good as the original. Fortunately for us, God told us how things will end - and he \textit{is} omniscient.

\begin{quotation}
The devil, who deceived them, was cast into the lake of fire and brimstone where the beast and the false prophet are. And they will be tormented day and night forever and ever. - Revelation 20:10
\end{quotation}



\begin{thebibliography}{9}
	{\footnotesize
		
	\bibitem{PlanetLabs} \url{https://www.planet.com/products/satellite-monitoring/}
	
	\bibitem{AIpredictsIntent} iSmart: AI Growth Marketing Agency, ``The Marketing Oracle: How AI Predicts Buyer Intent Before They Blink.'' May 7, 2025. https://ismartcom.com/blog/the-marketing-oracle-how-ai-predicts-buyer-intent-before-they-blink
	}
\end{thebibliography}

\end{multicols}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}





















}{den}