\chapter{Cleanup}
\thispagestyle{fancy}

It is important that things are put away in the correct and same spots each week. This is because of the following obvious and non-obvious reasons:

\begin{enumerate}[noitemsep, topsep=0pt]
	\item It ensures this documentation remains accurate.
	\item It makes things easy to find and account for.
	\item If we take any equipment outside of the building for use elsewhere, this ensures that nothing is forgotten or left behind.
\end{enumerate}

\begin{note}
Be sure to unplug all cables that were plugged in at the start. For cables that get rolled/coiled/bent, take caution to do so in the direction they naturally curve/bend to prevent kinks and unwanted bends. Use cable ties where appropriate to keep things neat and orderly.
\end{note}

\section{What Goes In The Laptop Bag}
\begin{enumerate}[noitemsep, topsep=0pt]
	\item Make sure the laptop is off bevfore closing the lid! The laptop goes in the small stretch pouch within the main pocket.
	\item The red HDMI cable and Timer go in the main pocket (not in the stretch pouch).
	\item The capture card gets wrapped in the bubble wrap and placed in the front pocket of the laptop bag - in the pocket with the index cards.
	\item The blue capture card cable and black timer cables get folded and placed in the other pocket of the laptop bag.
	\item The laptop charger (and associated cable - if detached) get placed in the front pocket of the laptop bag. 
\end{enumerate}


\section{What Goes In The Camera Box}
\begin{enumerate}[noitemsep, topsep=0pt]
	\item Make sure the camera lense is closed. The camera gets placed in the appropriate slot in the camera box where it fits.
	\item The small HDMI adapter, camera battery, small velcro strap, and camera charger all get placed in the other slot in the camera box.
\end{enumerate}


\section{What Goes In The Scarlett Focusrite Box}
\begin{enumerate}[noitemsep, topsep=0pt]
	\item The red scarlett box and gray scarlette USB cable get placed in the Focusrite box.
\end{enumerate}

\section{What Goes In The Tripod Bag}
\begin{enumerate}[noitemsep, topsep=0pt]
	\item The tripod.
\end{enumerate}


\section{What Goes In The Cabinet}
\begin{enumerate}[noitemsep, topsep=0pt]
	\item Everything that is ours gets placed in the cabinet. 
		\begin{enumerate}[noitemsep, topsep=0pt]
			\item The clear plastic tub fits nicely on the bottom shelf.
			\item The podium topper, the mic stand (just barely fits diagonally), and the tripod fit nicely on top of the clear tub. 
			\item The podium fits nicely on the second shelf.
			\item The scarlett box, camera box, laptop bag, and velcro strips fit nicely on the second shelf.
		\end{enumerate}
\end{enumerate}


\section{What Goes In The Back-Room}
Anything that was borrowed from the back room should be replaced where it was found in the back room. Assuming we need just the usual items, this should be the following:
\begin{enumerate}[noitemsep, topsep=0pt]
	\item The Audio cable goes in the blue tub with other audio cables.
\end{enumerate}
\begin{note}
While in the storage room, turn the Speaker power OFF. There is a large rack with a switch labeled ON/OFF (See Figure \ref{fig:speaker_power}). Turn this switch to the ON position.
\end{note}
