\chapter{Troubleshooting}
\thispagestyle{fancy}

This chapter covers common issues found during the sound setup. As issues arise and are fixed, they should be added to this chapter for future reference.

\section{Wifi Issues}

\begin{note}
	The credentials for the wifi login are the following:
	\\ NAME: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ \hspace{1cm} PASSWORD: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
\end{note}

\section{Sound Issues}

For all sound issues, the first step is to make sure all cables are plugged in the their correct spots. Sometimes cable connections can even be loose, so gently wiggle the connectors to make sure things are not just loosely connected.

\subsection*{The Laptop Sound Is Not Coming Out The Speakers}

When plugging in the audio jack into the laptop, make sure the `headphones' output option is selected in the window that appears. If a window does not appear, you can attempt to change the Windows audio settings. A system restart typically fixes this.

\section{Projector Issues}

\subsection*{The Laptop Is Not Showing On The Projector Screen}
\begin{enumerate}
	\item Ensure all cables are plugged in correctly.
	\item On the laptop, press the widow key and P. Select the \textit{Extend} mode.
\end{enumerate}

\section{Email Issues}

\subsection*{The Email Is Logged Out}

Login to the email.
\begin{note}
	The credentials for the email login are the following:
	\\ EMAIL: AustinUCGLaptop@gmail.com \hspace{1cm} PASSWORD: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
\end{note}

\subsection*{The Special Music Will Not Download}

Sometimes the special music (particularly when in video format saved to Google Drive) will appear as though it is not downloading. If you click the downlaod button multiple times and nothing changes (no status' or anything), it may be simply downloading silently in the background. Wait some time (maybe even 5-10 minutes depending on the size of the file) and see if the download finishes. When finished, it should display the file in the downloads dropdown or downloads folder.

\section{VLC Issues}

\subsection*{VLC Fullscreen Won't Stay On The Projector Screen}

Simply restart VLC and this issue should go away.