% Chapter 1 of 2 John\index{John}
\bookchapter{Greeting the Elect Lady}

\bverse The Elder, To the elect lady and her children, whom I love in truth, and not only I, but also all those who have known the truth,
\bverse because of the truth which abodes in us and will be with us forever:
\bverse Grace, mercy, \textit{and} peace will be with you from God the Father and from the Lord Jesus Christ, the son of the Father, in truth and love.

\bmarkerdown{Walk in Christ's Commandments}

\bverse I rejoiced greatly that I have found \textit{some} of your children walking in truth, as we received commandment from the Father.
\bverse And now I plead with you, lady, not as through I wrote a new commandment to you, but that which we have had from the beginning: that we love one another.
	\contextnote{}{He clearly states here that this is \textit{not} anything new, but something that has existed from the beginning and is just reiterating it in a different way.}

\bverse This is love, that we walk according to His commandments. This is the commandment, that as you have heard from the beginning, you should walk in it.

\bmarkerdown{Beware of Antichrist Deceivers}

\bverse For many deceivers have gone out into the world who do not confess Jesus Christ \textit{as} coming in the flesh. This is a deceiver and antichrist.
\bverse Look to yourselves, that we do not lose those things we worked for, but \that we may receive a full reward.
	\questionnote{}{Does this suggest that we can receive a \textit{partial} reward?}

\bverse Whoever transgresses and does not abide in the doctrine of Christ does not have God. He who abides in the doctrine of Christ has both the Father and the Son.
\bverse If anyone comes to you and does not bring this doctrine, do not receive him into your house nor greet him;
\bverse for he who greets him shares in his evil deeds.

\bmarkerdown{John's Farewell Greeting}

\bverse Having many things to write to you, I did not wish \textit{to do so} with paper and ink; but I hope to come to you and speak face to face, that our joy may be full.
\bverse The children of your elect sister greet you. Amen.
