\documentclass[10pt]{article}

%%% These are some packages that are useful
\usepackage{amsmath,amssymb, amscd,amsbsy, amsthm, enumerate}
\usepackage[export]{adjustbox}
\usepackage{lastpage}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[unicode]{hyperref}
\usepackage{tikz, pgfplots, xcolor, fancyhdr}
\usepackage{multicol,caption}
\usepackage{lipsum}
\usepackage[version=4]{mhchem}
\usepackage{float}
\usepackage{enumitem}

%%% Page formatting
%\setlength{\headsep}{30pt}
\setlength{\textheight}{9in}
\newcommand{\tab}{\hspace{1cm}}
%\setlength{\parindent}{25pt}

\title{Know Thy Enemy (Part 3) 	: The Old Gods}
\author{Antonius Torode}

%%% Header and Footer Info
\pagestyle{fancy}
\fancyhead[L]{{\large Template - \textbf{Change 03}}}
\fancyhead[C]{\today}
\fancyhead[R]{Name: Antonius Torode}


\fancyhf{} % sets both header and footer to nothing
\renewcommand{\headrulewidth}{0pt}
% your new footer definitions here

\fancyfoot[L]{}
\fancyfoot[C]{}
\fancyfoot[R]{\thepage\ of \pageref{LastPage}}

% Used to define spacing and format of References
\let\OLDthebibliography\thebibliography
\renewcommand\thebibliography[1]{
	\OLDthebibliography{#1}
	\setlength{\parskip}{0pt}
	\setlength{\itemsep}{0pt plus 0.3ex}
}

\newenvironment{Figure}
  {\par\medskip\noindent\minipage{\linewidth}}
  {\endminipage\par\medskip}


%%% Document Starts now
\begin{document}

\maketitle
\thispagestyle{fancy}


%\begin{abstract}
%TODO
%\end{abstract}

\begin{multicols}{2}

Throughout most of history and the ancient world, especially as seen in the Old Testament, humans interacted with various gods on a regular basis. Entire nations worshiped them, created idols in their image, and lived in ways to please them. In more modern times, at least here in America, we don't really think of there being various other gods. We know they existed in our history, but we would rarely consider that other individuals would be worshiping these gods from ancient times. Sometimes we even think of them as just small trinkets or idols that humans pretend to have power. What were the gods of old and where have they gone?

The Bible mentions a plethora of old gods:
\begin{quotation}
However every nation continued to make gods of its own, and put them in the shrines on the high places which the Samaritans had made, every nation in the cities where they dwelt. The men of Babylon made Succoth Benoth, the men of Cuth made Nergal, the men of Hamath made Ashima, and the Avites made Nibhaz and Tartak; and the Sepharvites burned their children in fire to Adrammelech and Anammelech, the gods of Sepharvaim. - 2 Kings 17:29-31
\end{quotation}
In other places we have mention of Baal\footnote{1 Kings 18:21 - ``And Elijah came to all the people, and said, `How long will you falter between two opinions? If the Lord is God, follow Him; but if Baal, follow him.' But the people answered him not a word.''}, Dagon\footnote{Judges 16:23 - ``Now the lords of the Philistines gathered together to offer a great sacrifice to Dagon their god, and to rejoice.''}, Marduk\footnote{Jeremiah 50:2 - ``Declare among the nations, Proclaim, and [a]set up a standard; Proclaim--do not conceal it--Say, ‘Babylon is taken, Bel is shamed. Merodach is broken in pieces; Her idols are humiliated, Her images are broken in pieces.''}, Molech\footnote{Leviticus 18:21 - ``And you shall not let any of your descendants pass through the fire to Molech, nor shall you profane the name of your God: I am the Lord.''}, and so many more. These old gods were worshiped not only just by individuals - but entire nations! Daily practices beliefs, and cultural practices were often influenced by these gods to define what day to day life would look like.

What were these old gods? Were they just inventions by man? Did us humans create them, dictate the rules they taught, and fabricate the practices they demanded? Was their only purpose to provide us humans with some ideology to follow - perhaps to serve some inner desire to worship a being higher than ourselves? If these old gods were nothing more than fictitious things we invented, what would be the harm in using them as a symbol of worship? What if we create ourselves a god which teaches nothing but \textit{good} principals - would that be okay? When you begin to study the many old gods of history, an interesting pattern emerges. It's fascinating that all of the ancient gods among all the cultures of old had eerily similar teachings. The things we consider `good' as Christians were typically not part of their teachings. On the contrary, the things we consider to be `bad' usually were. Perhaps this is because these `gods' were actually more sinister than we tend to think.

\begin{quotation}
\textit{I am the Lord your God}, who brought you out of the land of Egypt, out of the house of bondage. \textit{You shall have no other gods before Me}. - Exodus 20:2-3
\end{quotation}

The very first of the ten commandments tells us \textit{who is God} and to avoid \textit{any and every} other god. There is a very important reason for this.
\begin{quotation}
Rather, that the things which the Gentiles sacrifice they sacrifice \textit{to demons} and \textit{not} to God, and I do not want you to have fellowship with demons. - 1 Corinthians 10:20
\end{quotation}
These ancient gods are \textit{not} just trivial things we invented with no real power. They are \textit{demons}. Demons have power, influence, an agenda, and don't just exist in past generations. They trick people into worshiping them. They convince people to make idols of them and to live their lives in a way contrary to God's way. They convince us humans that they will gain benefit from living by \textit{their} rules. Though they don't just convince individuals, but entire nations.

As far as we can tell from the scriptures, demons don't live through just a single generation. Satan and his demons are described as being around from both the start of humanity all the way to the end times. Therefore, they were around in ancient times, and are still here now. So where is Baal? Where is Molech, and Ishtar? What are they up to? Are they perhaps just chilling in a cave somewhere relaxing? No. They are actively working. They are doing the same thing they've done throughout history - deceiving the nations and doing the works of their leader. These beings are \textit{not sitting idle}. So then where are they, and why do we not see them working around us?

This question is essentially what I discussed in my previous message \cite{part1}, which was intended to be a primer to this one. If we don't know our enemies, we will wonder where they are. But in contrast, if we \textit{do} know our enemies, we see them all around us.

Modern society, in many ways, is nothing like ancient times - and yet at the same time, is still very similar. Human beings have not changed much - but the environment around us has changed drastically. A thousand years ago, humans did not have the internet, social media, microwaves, airplanes, atom bombs, and so many more things. Life back then was slower paced, with less information, fewer connections\cite{Altruism}, more traditional practices, less individuality\cite{Altruism}, etc. Because of all these things, the tactics of our enemies have had to change and adapt. The forms they appeared in ancient times would not be effective in the modern age.

Imagine for a moment, if Molech came strolling into town, setup an altar, and advertised for people to come sacrifice their children to him. In exchange, their lives would be greatly improved. They would have more energy, time, and riches. They could spend more time on vacation - more time staying up late, partying, and just doing what they enjoy. Their children wouldn't have to suffer in this harsh world. They would not have to grow up poor, or deal with worry. All it would take is for them to just bring their child and sacrifice it to Molech. This was a common practice in many ancient cultures. 

I suspect that scenario would not get much traction in modern times. In fact, even the authorities of the land might step into a situation like that and completely shut down that altar of Molech. Now, consider if instead Molech simply convinced people that children aren't alive until they leave the womb of their mothers. Suppose he never setup an altar, but health clinics. Maybe he never even reveals himself, but instead presents it as the idea of the individuals. Suddenly, the same scenario is now accepted by many. It is now perceived as self-empowerment, a personal choice - but for all the same reasons.

\begin{thebibliography}{9}
	{\footnotesize
		
	\bibitem{part1} Torode, Antonius. \textit{Know Thy enemy (Part 1): The Unveiling}, March 2026. \url{https://github.com/torodean/bible-notes/blob/main/sermonettes/Know%20Thy%20Enemy/The%20Unveiling/The%20Unveiling.pdf}
	
	\bibitem{Altruism} Torode, Antonius. \textit{Altruism}, January 2023. \url{https://github.com/torodean/bible-notes/blob/main/sermonettes/Altruism/Altruism.pdf}
	}
\end{thebibliography}

\end{multicols}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}





















}{den}