\documentclass[9.5pt]{article}

%%% These are some packages that are useful
\usepackage{amsmath,amssymb, amscd,amsbsy, amsthm, enumerate}
\usepackage[export]{adjustbox}
\usepackage{lastpage}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[unicode]{hyperref}
\usepackage{tikz, pgfplots, xcolor, fancyhdr}
\usepackage{multicol}
\usepackage{lipsum}

%%% Page formatting
%\setlength{\headsep}{30pt}
\setlength{\textheight}{9in}
\newcommand{\tab}{\hspace{1cm}}
%\setlength{\parindent}{25pt}

\title{The Ultimate Conspirator}
\author{Antonius Torode}

%%% Header and Footer Info
\pagestyle{fancy}
\fancyhead[L]{{\large Template - \textbf{Change 03}}}
\fancyhead[C]{\today}
\fancyhead[R]{Name: Antonius Torode}


\fancyhf{} % sets both header and footer to nothing
\renewcommand{\headrulewidth}{0pt}
% your new footer definitions here

\fancyfoot[L]{}
\fancyfoot[C]{}
\fancyfoot[R]{\thepage\ of \pageref{LastPage}}

% Used to define spacing and format of References
\let\OLDthebibliography\thebibliography
\renewcommand\thebibliography[1]{
	\OLDthebibliography{#1}
	\setlength{\parskip}{0pt}
	\setlength{\itemsep}{0pt plus 0.3ex}
}

%%% Document Starts now
\begin{document}

\maketitle
\thispagestyle{fancy}

\begin{multicols}{2}

Each and every one of us has different things we like to talk about. We each have things we tend to discuss among our peers and we also have things we avoid discussing. One of my favorite topics that seems to be at the extremes of this scale is conspiracy theories. In this message, I'm going to discuss conspiracy theories. I'll start with a definition, give a few examples, explain why this topic is important, then give a biblically significant example to bring attention to the ultimate conspirator.

The purpose of this message is not to get everyone talking about conspiracy theories. The purpose is to demonstrate the importance of considering alternative ideas, information, and viewpoints without blindly dismissing things based solely on a label. I chose the topic of conspiracy theories to demonstrate this because they can represent the extremes of being completely fictitious to that of verifiable authentic ideas or scenarios - while simultaneously facing similar levels of societal skepticism. 

According to Merriam Webster Dictionary, a conspiracy theory is ``A theory that explains an event or set of circumstances as the result of a secret plot by usually powerful conspirators." Often times, when people hear this term, they completely ignore everything that follows. Some people hear this term and immediately think the person saying it is crazy. Other times, they believe everything and dive down a rabbit hole that will bury them. A while back, I gave a message on testing all things\cite{testAllThings} as Thessalonians states\footnote{``Test all things; hold fast what is good" - I Thessalonians 5:21}. When it comes to conspiracy theories, there's often much we can potentially learn by putting them to the test.

One example of a conspiracy theory is the flat earth theory. Humans have known the earth is round for thousands of years. Whether through geometrical reasoning, observations in astronomy, or more; it's not hard to show the earth is not flat. Personally, I know that if the earth was flat, none of the code I program at work would actually work. It's a simple thing to look into. 

Now imagine someone came up to you and said that all the light bulb manufacturer's were getting together and secretly reducing the life span of light bulbs to increase profits. Most people would think they are nuts. However, in 1924, a group of leading businessmen did just that. They gathered at Geneva for a meeting that altered the next few decades of the light bulb market. They created what was called the Phoebus Cartel, which became the first cartel in modern history (that we know of) to have a completely global reach\cite{lightbulbConspiracy}. 

The first example of flat earth shows that conspiracy theories can be completely non sensible - suggesting perhaps that they should be thrown out. The second example is something completely verifiable that is a recorded event in history. It demonstrates the opposite of the first - that conspiracy theories are both possible, and actually occur. The importance of contemplating this subject is to help understand the world around us, understanding the enemies around us, staying alert to what's happening around us, and maintaining a perspective of what reality both is or could be in order to put all things to the test.

\begin{quotation}
``11. Put on the whole armor of God, that you may be able to stand against the wiles\footnote{wiles (of the devil): cunning arts, deceit, craft, trickery} of the devil. 12. For we do not wrestle against flesh and blood, but against principalities\footnote{principalities: magistrate, power, principality, principle, rule}, against powers\footnote{powers: one who possesses authority; physical or mental, the power of rule or government}, against the rulers\footnote{rulers: the devil and his demons} of [c]the darkness of this age, against spiritual hosts of wickedness in the heavenly places." - Ephesians 6: 11-12 (NKJV)
\end{quotation}

Now, as a more current example, consider an organization (whom I won't mention by name yet). This organization is considered by some to be ``The largest and most influential organization in the world \cite{Oakridge}." According to their own website, they are ``the world’s only truly universal global organization", which "has become the foremost forum to address issues that transcend national boundaries \cite{UNPreamble}." This organization has supporters and ties of all sort, including but not limited to The Rockefeller foundation, Bill \& Melinda Gates Foundation, Johnson \& Johnson, Verizon, Disney, and many more. Clearly this organization is very powerful and influential. 

There's a conspiracy theory involving this organization that claims they are heavily connected with Satan Influence/Worship. This theory suggests that this influence comes through another consulting organization called the Lucis Trust. The Lucis trust has their headquarters within this organization's building. They also have Consultative Status with the Economic and Social Council of the organization. They play an active role in the organization where they give their support through meditation, educational materials, presentations, discussions, videos, seminars, suggestions for action, and more. They even participate in organization events, contributes to policy discussions, and engage with member states. Clearly, the Lucis Trust has close ties to this organization \cite{LTAboutUs}.

If you were to look into this conspiracy theory, you'd find a lot of old looking .com websites. Many of which have donation links, and don't look too credible on their surface. Even if you ask ChatGPT, an AI, about Lucis Trust, it states they are ``not associated with Satan." However, if you go straight to the source, the Lucis Trust website, you may get a different picture.

\begin{quotation}
``The activities of the Lucis Trust promote the education of the human mind towards recognition and practice of the spiritual principles and values upon which a stable and interdependent \textbf{world society} may be based.” \cite{LTAboutUs}
\end{quotation}

\begin{quotation}
``In the theosophical perspective, the descent of these solar Angels was not a fall into sin or disgrace but rather an \textbf{act of great sacrifice}, as is suggested in the name “Lucifer” which means light-bearer.” \cite{LTAboutUs}
\end{quotation}

\begin{quotation}
“The Solar Gods are the Fallen Angels.” … “They are the Serpents of Wisdom.” … “Their nature is Knowledge and Love.” \cite{LTAboutUs}
\end{quotation}

Reading through their source materials gives a picture of fallen angels that present themselves as light bringers and beings of spiritual good. It's clear from biblical scripture that this is the way Satan works.

\begin{quotation}
``... for Satan himself transforms himself into an angel of light.” - 2 Corinthians 11:13
\end{quotation}

There is even a common phrase used within the Lucis Trust source material which is familiar to any biblical scholar. 

\begin{quotation}
``This is the work of the New Group of World Servers and the intelligent men of goodwill. \textbf{Their name is Legion.}” \cite{LTAboutUs}
\end{quotation}

In Mark 5:9, we see a conversation between Jesus and the demons that possessed a man. The demons make a claim using the same wording.

\begin{quotation}
9. Then Jesus asked him, “What is your name?”
“My name is Legion,” he replied, “for we are many.
\end{quotation}

It's clear from these examples, that this organization that I have yet to name may be closer connected to the influence of dark forces than not. So how does this effect us? That un-named organization that I mentioned before is actually a very familiar thing known as the United Nations. This is a corporation that has ties all over the globe. Therefore, it can potentially effect us all in some way. So what should we do with this information? Sometimes it's better to just be aware of things. We cannot truly know what we're up against if we remain ignorant to reality. This topic simply serves as an example to inform us of the potential forces working all around us. Going back to our scripture in Ephesians, we then know why it's so important to ``put on the whole armor of God, that you may be able to stand against the wiles of the devil. 12 For we do not wrestle against flesh and blood, but against principalities, against powers, against the rulers of [c]the darkness of this age, against spiritual hosts of wickedness in the heavenly places."

\begin{thebibliography}{9}
	{\footnotesize
	
	\bibitem{testAllThings} Torode, Antonius, Test All Things (April 2023), https://torodean.github.io/sermonettes.html
	
	\bibitem{lightbulbConspiracy} M. Krajewski, "The great lightbulb conspiracy," in IEEE Spectrum, vol. 51, no. 10, pp. 56-61, October 2014, doi: 10.1109/MSPEC.2014.6905492.
	
	\bibitem{Oakridge} https://www.oakridgemun.in/
	
	\bibitem{UNPreamble} https://www.un.org/en/about-us/un-charter/preamble
	
	\bibitem{LTAboutUs} https://www.lucistrust.org/
	}
\end{thebibliography}

\end{multicols}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}





















