\documentclass[10pt]{article}

%%% These are some packages that are useful
\usepackage{amsmath,amssymb, amscd,amsbsy, amsthm, enumerate}
\usepackage[export]{adjustbox}
\usepackage{lastpage}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[unicode]{hyperref}
\usepackage{tikz, pgfplots, xcolor, fancyhdr}
\usepackage{multicol,caption}
\usepackage{lipsum}
\usepackage[version=4]{mhchem}
\usepackage{float}

%%% Page formatting
%\setlength{\headsep}{30pt}
\setlength{\textheight}{9in}
\newcommand{\tab}{\hspace{1cm}}
%\setlength{\parindent}{25pt}

\title{Seduced By Statistics}
\author{Antonius Torode}

%%% Header and Footer Info
\pagestyle{fancy}
\fancyhead[L]{{\large Template - \textbf{Change 03}}}
\fancyhead[C]{\today}
\fancyhead[R]{Name: Antonius Torode}


\fancyhf{} % sets both header and footer to nothing
\renewcommand{\headrulewidth}{0pt}
% your new footer definitions here

\fancyfoot[L]{}
\fancyfoot[C]{}
\fancyfoot[R]{\thepage\ of \pageref{LastPage}}

% Used to define spacing and format of References
\let\OLDthebibliography\thebibliography
\renewcommand\thebibliography[1]{
	\OLDthebibliography{#1}
	\setlength{\parskip}{0pt}
	\setlength{\itemsep}{0pt plus 0.3ex}
}

\newenvironment{Figure}
  {\par\medskip\noindent\minipage{\linewidth}}
  {\endminipage\par\medskip}


%%% Document Starts now
\begin{document}

\maketitle
\thispagestyle{fancy}


\begin{abstract}
TODO
\end{abstract}

\begin{multicols}{2}


\begin{quotation}
``Deliver my soul, O Lord, from lying lips \textit{And} from a deceitful tongue.'' - Psalm 120:2 (NKJV)
\end{quotation}

Lying is not the same as deceit. If someone tells you a lie, you may realize it, but if someone deceives you, you will not know. For if you realize it, then you are no longer deceived. Deceit is a tool used by the evil. It's a powerful tool. It allows evil to masquerade as good - as an angel of light. 

\begin{quotation}
``Deceit is in the heart of those who devise evil.'' - Proverbs 12:20 (NKJV)
\end{quotation}

Deception is something that we all need to be aware of. We need to understand that it's all around us, and it's targeting us continually in our everyday lives. But deceit is not something which is always easy to catch. Sometimes, it appears as kind, genuine, or even as something obvious and trustworthy. That is why deception is such a powerful tool.  

\begin{quotation}
``He who hates, disguises \textit{it} with his lips, And lays up deceit within himself. When he speaks kindly, do not believe him, For \textit{there are} seven abominations in his heart; \textit{Though his} hatred is covered by deceit.'' - Proverbs 26:24-26 (NKJV)
\end{quotation}

Consider the end time Babylon. A great city which reigns over the kings of the earth\footnote{Revelation 17:18 - ``And the woman whom you saw is that great city which reigns over the kings of the earth.''}. A city of gold and precious stones - clothed in fine linen, purple, and scarlet. But how does Babylon get this way?

\begin{quotation}
``The light of a lamp shall not shine in you anymore, and the voice of bridegroom and bride shall not be heard in you anymore. For your merchants were the great men of the earth, for by your sorcery all the nations were deceived.'' - Revelation 18:23
\end{quotation}

By her sorcery, all the nations will be deceived. But what is sorcery? The word `sorcery' here is the greek word \textit{pharmakeia} \cite{pharmakeia}. Pharmakeia is commonly translated to \textit{sorcery} or \textit{witchcraft}, but the Lexical definitions from Bible concordances are as follows:
\begin{enumerate}\itemsep0em 
\item the use or the administering of drugs.
\item poisoning ("pharmacy").
\item (metaphorically) the deceptions and seductions of idolatry.
\end{enumerate}
With everything we know about Babylon, the third definition likely fits the best, but all three of these most likely fit in some way, shape, or form. For drugs are a way of seductions. Drugs are very much a form of idolatry. But are drugs a tool of deception? This is a question which can be explored to show just how dangerous the tool of deception can be.

First, can drugs have a global impact? Do the effects of (for example) pharmacies and pharmaceuticals (a subset of \textit{drugs} as a category) have the reach capable of deceiving nations? A good way to demonstrate that is the case is to follow the money. Our world is controlled by money, which is a topic for another time - but if the pharmaceutical industry 

\begin{thebibliography}{9}
	{\footnotesize
		
	\bibitem{pharmakeia} \url{https://biblehub.com/greek/5331.htm}
	
	\bibitem{godrules} \url{https://godrules.net/library/strongs2b/gre5331.htm}
	
	}
\end{thebibliography}

\end{multicols}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}





















}{den}