% Chapter 1 of 1 John\index{John}
\bookchapter{What Was Heard, Seen, and Touched}

\bverse That which was from the beginning, which we have heard, which we have seen with our eyes, which we have looked upon, and our hands have handled, concerning the Word of life--
\bverse the life was manifested, and we have seen, and bear witness, and declare to you that eternal life which was with the Father and was manifested to us--
\bverse that which we have seen and heard we declare to you, that you also may have fellowship with us; and truly our fellowship \textit{is} with the Father and with His Son Jesus Christ.
\bverse And these things we write to you that your joy may be full.

\bmarkerdown{Fellowship With Him and One Another}

\bverse This is the message which we have heard from Him and declare to you, that God is light and in Him is no darkness at all.
\bverse If we say that we have fellowship with Him, and walk\vmark{a} in darkness, we lie and do not practice the truth.
	\doctrinenote{a}{It is very clear that \textit{walking} (or taking actions, living in, etc) in darkness (sin or actions against God whom is light as explained in \bref{1 John 1:5}) is something we cannot have any part of - otherwise we do \textit{not} have fellowship with Christ.}

\bverse But if we walk\vmark{a} in the light as He is in the light, we have fellowship with one another, and the blood of Jesus Christ His Son cleanses us from all sin.
	\doctrinenote{a}{Actions (implying a literal doing and not just believing) are clearly required to be part of having fellowship with Jesus. This action (\textit{walking}) is a requirement for Jesus Christ to cleanse us from sin - it requires action on our part.}

\bverse If we say that we have no sin, we deceive ourselves, and the truth is not in us.
\bverse If we confess our sins, He is faithful and just to forgive us \textit{our} sins and to cleanse us from all unrighteousness.
\bverse If we say that we have not sinned, we make Him a liar, and His word is not in us.
	\doctrinenote{}{A huge part of having our sins cleansed (as explained in \bref{1 John 5:7}) is recognizing that we have and live in sin. We have to recognize and confess these, or we are deceiving ourselves. If we do not recognize this, we therefore do not have an understanding of reality.}

