% Chapter 5 of 1 John
\bookchapter{Obedience by Faith}

\bverse Whoever believes that \name{Jesus} is the Christ is born of God, and everyone who loves Him who begot also loves him who is begotten of Him.
\bverse By this we know that we love the children of God, when we love God and keep his commandments.
\bverse For this is the love of God, that we keep His commandments. And His commandments are not burdensome.
\bverse For whatever is born of God overcomes the world. And this is the victory that has overcome the world--our faith.
\bverse Who is he who overcomes the world, but he who believes that \name{Jesus} is the Son of God.
	\generalnote{}{This is a prerequisite but obviously (as outlined in the previous scriptures) not the only requirement.}
	
\bmarkerdown{The Certainty of God's Witness}
	
\bverse This is He who came by water and blood--\name{Jesus Christ}; not only bt water, but by water and blood. And it is the Spirit who bears witness, because the Spirit who bears witness, because the Spirit is truth.
\bverse \st{For there are three that bear witness in heaven: the Father, the Word, and the Holy Spirit; and these three are one.}
\bverse \st{And there are three that bear witness on earth: the Spirit, the water, and the blood; and these three agree as one.}
	\contextnote{}{Many translations omit these verses (1 John 5:7-8) because it is believed to have been added (see below notes).}
	\translationnote{}{These verses do not appear in manuscripts until about the fourteenth or fifteenth centuries\cite{1john57addition}.}
	
\bverse If we receive the witness of men, the witness of God is greater; for this is the witness of God which He has testified of His Son.
\bverse He who believes in the Son of God has the witness in himself; he who does not believe God has made Him a liar, because he has not believed the testimony that God has given of His Son.
\bverse And this is the testimony: that God has given us eternal life, and this life is in His Son.
\bverse He who has the Son has life; he who does not have the Son of God does not have life.
\bverse These things I have written to you who believe in the name of the Son of God, that you may know that you have eternal life, and that you may \textit{continue to} believe in the name of the Son of God.

\bmarkerdown{Confidence and Compassion in Prayer}

\bverse Now this is the confidence that we have in Him, that if we ask anything according to His will\bmarker{a}, He hears us.
	\contextnote{a}{This is an important addition to the commonly known `ask and you shall receive' belief. The \textit{ask} must be according to His will in order to be fulfilled, which means if you ask things \textit{not} according to His will, there is no guarantee He hears us.}

\bverse And if we know that He hears us, whatever we ask, we know that we have the petitions that we have asked of Him.
\bverse If anyone sees his brother sinning a sin \textit{which does} not \textit{lead} to death, he will ask, and He will give him life for those who commit sin not \textit{leading} to death. There is sin \textit{leading} to death. I do not say that he should pray about that.
\bverse All unrighteousness is sin and there is sin not \textit{leading} to death.
	\questionnote{}{How do these two versus relate to \bref{Romans 6:23}, where it says the wages of sin \is death and \bref{1 John 3:4}.}

\bmarkerdown{Knowing the True-Rejecting the False}

\bverse We know that whoever is born of God does not sin; but he who has been born of God keeps himself, and the wicked one does not touch him.
\bverse We know that we are of God, and the whole world lies \textit{under the sway of} the wicked one.
	\generalnote{}{This clearly states that the \textit{whole} world is under the sway of the Devil and his demons \textit{except}, those who are born of God. The only defense against the dark forces of this world are through God. This closely relates to \bref{Mathew 12:43} to \bref{Mathew 12:45}, where evil spirits can inhabit people who do not have God's spirit in them (thus being an empty house). This leaves them open to the influences of evil.}

\bverse And we know that the Son of God has come and has given us an understanding, that we may know Him who is true; and we are in Him who is true, in His Son Jesus Christ. This is the true God and eternal life.
\bverse Little children, keep yourselves from idols. Amen.
	\contextnote{}{At first, this verse seems a bit out of context with the rest of the section and just `tacked-onto' the end as another relevant note to the area. After closer consideration it like \is relevant to the area but also closely related to the section. It's very clear that the \textit{wicked one} and evil spirits are very big on symbolism and idolatry. Idolatry takes the focus away from God and puts us humans essentially under a \textit{spell}, where we are then \textit{under the wicked one}, or \textit{possessed} in a way. The idols are directly linked to this, because they are a means to an end for evil. Therefore, keeping away from idols will directly help us to keep the wicked one from touching us by taking away his power and influences.}
