% Chapter 4 of 1 John\index{John}
\bookchapter{Love for God and One Another}

\bverse Beloved, do not believe every spirit, but test the spirits, whether they are of God; because many false prophets have gone out into the world.
	\generalnote{}{Notice here that \textit{spirits} are used when explaining that false prophets have gone into the world. Do \textit{spirits} here represent any spirit (man, animal, etc) or could this be referring to only \textit{spirit beings}. This could imply that many of the false prophets are demonic \textit{spirits} which is supported in \bref{1 John 4:3}.}

\bverse By this you know the Spirit of God: Every spirit that confesses that \name{Jesus Christ} has come in the flesh is of God, 
\bverse and Every spirit that does not confess that \name{Jesus Christ} has come in the flesh is not of God\vmark{a}. And this is the \name{spirit} of the Antichrist, which you have heard was coming, and is now already in the world\vmark{b}.
	\generalnote{a}{There are many groups of people who deny this, such as many modern day Jews. But if anyone claims this, they are not of God. This is a good litmus test.}
	\generalnote{b}{This was written a long time ago, and therefore this \textit{spirit} must not be a physical being, but rather a \textit{spiritual entity}. Therefore, the Antichrist is a demonic being - perhaps \name{Satan} himself.}

\bverse You are of God, little children, and have overcome them, because He who is in you is greater than he who is in the world\vmark{a}.
	\generalnote{a}{This could be interpreted as he who is in \name{Jesus} is greater than he who is Antichrist (Literally meaning, anti-christ since the Antichrist is \textit{in the world} per the previous few scriptures). The distinction of `in' the world and `of' the world is the physical vs spiritual distinction here. He who is of the world would be he who is of the spirit of the Antichrist.}

\bverse They are of the world. Therefore they speak \textit{as} of the world, and the world hears them.
\bverse We are of God. He who knows God hears us; he who is not of God does not hear us\vmark{a}. By this we know the spirit of truth and the spirit of error\vmark{b}.
	\generalnote{a}{There is such a distinction between Christ and Antichrist, that people who are not of Christ cannot even understand or comprehend those of Christ. This shows that there will be confusion between the two groups.}
	\generalnote{b}{The spirit of truth is Christ and the spirit of Error is anti-christ. To be anti-christ means to not be in the truth and to instead be in error.}

\bmarkerdown{Knowing God Through Love}

\bverse Beloved, let us love one another, for love is of God; and everyone who loves is born of God and knows God.
	\generalnote{}{This is why there is such a large attack and distortion of love in the modern day society. If you cannot know what love is then you cannot distinguish between a godly spirit and the spirit of the Antichrist.}

\bverse He who does not love does not know God, for God is love.
\bverse In this the love of God was manifested toward us, that God has sent His only begotten Son into the world, that we might live through Him.
\bverse In this is love, not that we loved God, but that He loved us and sent His son \textit{to be} the propitiation\vmark{a} for our sins.
	\translationnote{a}{The English definition of propitiation is `the act of gaining or regaining the favor or goodwill of someone or something.'}

\bverse Beloved, if God so loved us, we also ought to love one another.

\bmarker{Seeing God Through Love}

\bverse No one has seen God at any time. If we love one another, God abides in us, and His love has been perfected in us.
\bverse By this we know that we abide in Him, and He in us, because He has given us of His Spirit.
\bverse And we have seen and testify that the Father has sent the Son \textit{as} Savior of the world. 
\bverse Whoever confesses that Jesus is the Son of God, God abides in him, and he in God.
	\generalnote{}{To confess is much more than to simply accept it. If you truly confess, you accept it and understand the meaning of it, which includes following the commandments and teachings of Jesus.}

\bverse And we have known and believed the love that God has for us. God is love, and he who abides in love abides in God, and God in him.

\bmarkerdown{The Consummation of Love}

\bverse Love has been perfected among us in this: that we may have boldness in the day of judgment; because as He is, so are we in this world.
\bverse There is no fear in love; but perfect love casts out fear, because fear involves torment. But he who fears has not been made perfect in love.
\bverse We love Him because He first loved us.

\bmarkerdown{Obedience by Faith}

\bverse If someone says, ``I love God,'' and hates his brother, he is a liar; for he who does not love his brother whom he has seen, how can he love God whom he has not seen?
\bverse And this commandment we have from Him: that he who loves God \textit{must} love his brother also.
