% Chapter 2 of 1 John\index{John}
\bookchapter{The Test of Knowing Christ}

\bverse My little children, these things I write to you, so that you may not sin\vmark{a}. And if anyone sins, we have an Advocate with the Father, Jesus Christ the righteous\vmark{b}.
	\doctrinenote{a}{One of the main purposes of this letter (as stated here) is so that we understand that we should \textit{not} sin. If sinning was okay, this would not really serve a purpose. It further clarifies that the law \textit{has to} be physically followed and our actions matter. If they did not, there would be no reason to not sin.}
	\doctrinenote{b}{Jesus is our advocate with the Father. When we inevitably sin, because we all do, He is the one who we have to go to in order to reconcile what we've done. This is pivotal, as explained in \bref{1 John 5:7}.}

\bverse And He Himself is the propitiation for our sins, and not for ours only but also for the whole world.

\bmarkerdown{The Test of Knowing Him}

\bverse Now by this we know that we know Him, if we keep His commandments.
	\doctrinenote{}{This again reiterates the actions of \textit{doing} the commandments in order to know Him. If we do not do this, we have no ability to understand who Jesus Christ really was.}

\bverse He who says, ``I know Him,'' and does not keep His commandments, is a liar, and the truth is not in him.
	\doctrinenote{}{It is therefore impossible to know Jesus Christ without keeping his commandments.}

\bverse But whoever keeps His word, truly the love of God is perfected in him. By this we know that we are in Him.
\bverse He who says he abides in Him ought himself also walk just as He walked.
	\contextnote{}{Jesus kept all of the commandments. This is how he \textit{walked}. This is directly referring to His actions and how He lived His life.}

\bverse Brethren, I write no new commandment to you, but an old commandment which you have had from the beginning\vmark{a}. The old commandment is the word which you heard from the beginning.
	\contextnote{a}{These things that are being said are \textit{not} new. These are the same commandments that have always existed and no different. Anything that seems different is simply a misrepresentation of the original commandments which have always existed (from the beginning).}

\bverse Again, a new commandment I write to you\vmark{a}, which thing is true in Him and you, because the darkness is passing away, and the true light is already shining.
	\contextnote{a}{This is a little confusing. At first he says he is not giving any new commandment, but an old commandment which they have had from the beginning. Now he says that he is giving a new commandment. The commandment here is not new in the sense that it has always existed. The \textit{new} part comes from the new realization, depth, and meaning that this commandment is presented in through Jesus Christ's teaching. In a sense, it's saying that we've had this commandment all along, but we didn't really understand if fully - so it seems new even though we've had it all along.}

\bverse He who says he is in the light, and hates his brother, is in darkness until now.
\bverse He who loves his brother abides in the light, and there is no cause for stumbling in him.
\bverse But he who hates his brother is in darkness and walks in darkness, and does not know where he is going, because the darkness has blinded his eyes.

\bmarkerdown{Their Spiritual State}

\begin{bquotation}
\bverse I write to you, little children, Because your sins are forgiven you for His name's sake.
\bverse I write to you, fathers, Because you have known Him \textit{who} is from the beginning. I write to you, young men, Because you have overcome the wicked one. I write to you, little children, Because you have known the Father.
\bverse I have written to you, fathers, Because you have known Him \textit{who} is from the beginning. I have written to you, young men, Because you are strong, and the word of God abides in you, And you have overcome the wicked one.
\end{bquotation}

\bmarkerdown{Do Not Love the World}

\bverse Do not love the world or the things in the world. If anyone loves the world, the love of the Father is not in him.
\bverse For all that \textit{is} in the world--the lust of the flesh, the lust of the eyes, and the pride of life--is not of the Father but is of the world.
\bverse  And the world is passing away, and the list of it; but he who does the will of God abides forever.

\bmarkerdown{Deceptions of the Last Hour}

\bverse Little children, it is the last hour; and as you have heard that the Antichrist is coming, even now many Antichrists have come, by which we know that it is the last hour.
\bverse They went out from us, but they were not of us; for if they had been of us, they would have continued with us; but \textit{they went out} that they might be made manifest, that none of them were of us.
\bverse But you have an anointing from the Holy One, and you know all things. 
\bverse I have not written to you because you do not know the truth, but because you know it\vmark{a}, and that no lie is of the truth.
	\contextnote{a}{The audience of this letter \textit{knows} the truth, they are not ignorant of it.}

\bverse Who is a liar but he who denies that Jesus is the Christ? He is Antichrist who denies the Father and the Son.
\bverse Whoever denies the Son does not have the Father either; he who acknowledges the Son has the Father also.

\bmarkerdown{Let Truth Abide in You}

\bverse Therefore let that abide in you which you heard from the beginning. If what you heard from the beginning abides in you, you also will abide in the Son and in the Father.
\bverse And this is the promise that He has promised us--eternal life.
\bverse These things I have written to you concerning those who \text{try to} deceive you.
\bverse But the anointing which you have received from Him abides in you, and you do not need that anyone teach you; but as the same anointing teaches you concerning all things, and is true, and is not a lie, and just as it has taught you, you will abide in Him.

\bmarkerdown{The Children of God}

\bverse And now, little children, abide in Him, that when He appears, we may have confidence and not be ashamed before Him at His coming.
\bverse If you know that He is righteous, you know that everyone who practices righteousness is born of Him.
