% Chapter 5 of Genesis
\bookchapter{The Family Of Adam}


\bverse This is the book of the genealogy\vmark{a} of Adam. In the day that God created man, He made him in the likeness of God.
	\contextnote{a}{Only the names of those leading to the genealogy of Noah are given. The others are not mentioned, but it is implied they exist in \bref{Genesis 5:4}, \bref{Genesis 5:7}, \bref{Genesis 5:10} and other scriptures.}

\bverse He created them male and female, and blessed them and called them Mankind in the day they were created.
\bverse And Adam lived one hundred and thirty years, and begot \textit{a son} in his own likeness, after his image, and named him Seth.
\bverse After he begot Seth, the days of Adam were eight hundred years; and he had sons and daughters.
\bverse So all the days that Adam lived were nine hundred and thirty years; and he died.
\bverse Seth lived one hundred and five years, and begot Enosh.
\bverse After he begot Enosh, Seth lived eight hundred and seven years, and had sons and daughters.
\bverse So all the days of Seth were nine hundred and twelve years; and he died.
\bverse Enosh lived ninety years, and begot Cainan.
\bverse After he begot Cainan, Enosh lived eight hundred and fifteen years, and had sons and daughters.
\bverse So all the days of Enosh were nine hundred and five years; and he died.
\bverse Cainan lived seventy years, and begot Mahalalel.
\bverse After he begot Mahalalel, Cainan lived eight hundred and forty years, and had sons and daughters.
\bverse So all the days of Cainan were nine hundred and ten years; and he died.
\bverse Mahalalel lived sixty-five years, and begot Jared. After he begot Jared, Mahalalel lived eight hundred and thirty years, and had sons and daughters. So all the days of Mahalalel were eight hundred and ninety-five years; and he died.
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
