% Chapter 25 of Genesis
\bookchapter{\Abraham and \name{Keturah}}

\bverse \Abraham again took a wife\vmark{a}, and her name \was \name{Keturah}.
	\contextnote{a}{Taking multiple wives seemed to be a fairly common practice in these times.}

\bverse And she bore him \name{Zimran}, \name{Jokshan}, \name{Medan}, \name{Midian}, \name{Ishbak}, and \name{Shuah}.
\bverse \name{Jokshan} begot \name{Sheba} and \name{Dedan}. And the sons of \name{Dedan} were \name{Asshurim}, \name{Letushim}, and \name{Leummim}.
\bverse And the sons of \name{Midian} \were \name{Ephah}, \name{Epher}, \name{Hanoch}, \name{Abidah}, and \name{Eldaah}. All these \were the children of \name{Keturah}.

\todo{Make a family tree diagram out of \Abraham and \name{Keturah}.}

\bverse And \Abraham gave all that he had to \Isaac.
\bverse But \Abraham gave gifts to the sons of the concubines which \Abraham had; and while he was still living he sent them eastward, away from \Isaac his son, to the country of the east.

\bmarkerdown{\Abraham's Death and Burial}

\bverse This \textit{is} the sum of the years of \Abraham's life which he lived: one hundred and seventy-five years.
\bverse Then \Abraham breathed his last and died in a good old age, and old man and full of \textit{years}, and was gathered to his people.
\bverse And his sons \Isaac and \name{Ishmael} buried him in the cave of \location{Machpelah}, which \textit{is} before \location{Mamre}, in the field of \name{Ephron} the son of \name{Zohar} the \people{Hittite},
\bverse the field which \Abraham purchased from the sons of \name{Heth}. There \Abraham was buried, and \Sarah his wife.
\bverse And it came to pass, after the death of \Abraham, that God blessed his son \Isaac. And \Isaac dwelt at \location{Beer Lahai Roi}.

\bmarkerdown{The Families of \name{Ishmael} and \Isaac}

\bverse Now this \textit{is} the  genealogy of \name{Ishmael}, \Abraham's son, whom \name{Hagar} the \people{Egyptian}, \Sarah's maidservant, bore to \Abraham.
\bverse And these \were the names of the sons of \name{Ishmael}, by their names, according to their generations: The firstborn of \name{Ishmael}, \name{Nebajoth}; then \name{Kedar}, \name{Abdeel}, \name{Mibsam},
\bverse \name{Mishma}, \name{Dumah}, \name{Massa},
\bverse \name{Hadar}, \name{Tema}, \name{Jetur}, \name{Naphish}, and \name{Kedemah}.

\todo{Make a family tree diagram of \name{Ishmael}'s genealogy.}

\bverse These \were the sons of \name{Ishmael} and these \were their names, by their towns and their settlements, twelve princes according to their nations.
\bverse These \were the years of the life of \name{Ishmael}: one hundred and thirty-seven years; and he breathed his last and died, and was gathered to his people.
\bverse (They dwelt from \location{Havilah} as far as \location{Shur}, which is east of \location{Egypt} as you go toward \location{Assyria}.) He died in the presence of all his brethren.
\bverse This \textit{is} the genealogy of \Isaac, \Abraham's son. \Abraham begot \Isaac. \Isaac was forty years old when he took \Rebekah as wife, the daughter of \name{Bethuel} the \people{Syrian} of \location{Padan Aran}, the sister of \name{Laban} the \people{Syrian}.
\bverse Now \Isaac pleaded with the \lord for his wife, because she \was barren; and the \lord granted his plea, and \Rebekah his wife conceived.
\bverse But the children struggled together within her; and she said, ``If \textit{all is} well, why \textit{am} I \textit{like} this?'' So she went to inquire of the \lord.
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
