% Chapter 6 of Genesis
\bookchapter{The Wickedness And Judgment\index{Judgment} of Man}


\bverse Now it came to pass, when men began to multiply on the face of the earth\index{Earth}, and daughters were born to them,
\bverse that the sons\vmark{a} of God saw the daughters of men, that they \textit{were} beautiful; and they took wives for themselves of all whom they chose.
	\translationnote{a}{The word `sons' here (Strong's 1121\cite{Strong's GodRules}) means children, people, grandsons, youth, etc. Since Adam\index{Adam} was directly created by God, any of his descendants could fall into this category. The `sons of God' distinction could be used to specifically refer to people who were following Gods and not those who strayed from his ways.}

\bverse And the \lord said, ``My Spirit shall not strive with man forever, for he \textit{is} indeed flesh; yet his days shall be one hundred and twenty years.''
	\contextnote{}{Since it is obvious that the days of man were much longer than 120 throughout the prior parts of Genesis, this must be setting up and explaining the time after the flood (as also seen in the next verse).}

\bverse There were giants\vmark{a} on the earth\index{Earth} in those days, and also afterward\vmark{b}, when the sons of God\vmark{c} came in to the daughters of men and they bore \textit{children} to them. Those \textit{were} the mighty men who \textit{were} of old, men of renown.
	\translationnote{a}{This term for `giant' (Strong's 5303\cite{Strong's GodRules}), is also known as `the Nephilim' has a bit of debate around it. Regardless, it means that there were a group of people with unusually large size and strength.}
	\contextnote{b}{This is likely referring to after the flood, since we also see giants mentioned after this time period in \bref{Numbers 13:33}.}
	\philosophicalnote{c}{Some argue that the `sons of God' here is angels (or demons), and thus the spirit beings created offspring with humans. The word for sons here does not really fit that at all (see the note on \bref{Genesis 6:2}).}

\bverse Then the \lord saw that the wickedness of man \was great in the earth\index{Earth}, and \that every intent of the thoughts of his heart \was only evil continually.
\bverse And the \lord was sorry that He had made man on the earth\index{Earth}, and He was grieved in His heart.
\bverse So the \lord said, ``I will destroy man whom I have created from the face of the earth\index{Earth}, both man and beast, creeping thing and birds of the air, for I am sorry that I have made them.''
\bverse But Noah\index{Noah} found grace\index{Grace} in the eyes of the \lord.

\bmarkerdown{Noah Pleases God}

\bverse This is the genealogy of Noah\index{Noah}. Noah\index{Noah} was a just man, perfect in his generations. Noah\index{Noah} walked with God.
\bverse And Noah\index{Noah} begot three sons: Shem, Ham, and Japheth.
\bverse The earth\index{Earth} also was corrupt before God, and the earth\index{Earth} was filled with violence.
\bverse So God looked upon the earth\index{Earth}, and indeed it was corrupt; for all flesh had corrupted their way on the earth\index{Earth}.

\bmarkerdown{The Ark\index{Ark} Prepared}

\bverse And God said to Noah\index{Noah}, ``The end of all flesh has come before Me, for the earth\index{Earth} is filled with violence through them; and behold, I will destroy them with the earth\index{Earth}.
\bverse Make yourself an ark\index{Ark} of gopherwood; make rooms in the ark\index{Ark}, and cover it inside and outside with pitch.
\bverse And this is how you shall make it: The length of the ark\index{Ark} \textit{shall} be three hundred cubits\vmark{a}, its width fifty cubits, and its height thirty cubits.
	\contextnote{a}{A cubit is an ancient unit of length, approximately equal to the distance from the elbow to the tip of the middle finger. It is approximately 18 inches. This would make the ark\index{Ark} about 450 ft $\times$ 75 ft $\times$ 45 ft}

\bverse You shall make a window for the ark\index{Ark}, and you shall finish it to a cubit from above; and set the door of the ark\index{Ark} in its side. You shall make it \textit{with} lower, second, and third decks.
\bverse And behold, I Myself am bringing floodwaters on the earth\index{Earth}, to destroy from under heaven\index{Heaven} all flesh in which \textit{is} the breath\index{Breath} of life; and everything that \textit{is} on the earth\index{Earth} shall die.
\bverse But I will establish My covenant\index{Covenant} with you; and you shall go into the ark\index{Ark}--you, your sons, your wife, and your sons' wives with you.
\bverse And of every living thing of all flesh you shall bring two of every \textit{sort} into the ark\index{Ark}, to keep \textit{them} alive with you; they shall be male and female.
\bverse Of the birds after their kind, of animals after their kind, and of every creeping thing of the earth\index{Earth} after its kind, two of every \textit{kind} will come to you to keep \textit{them} alive.
\bverse And you shall take for yourself of all food that is eaten, and you shall gather \textit{it} to yourself; and it shall be food for you and for them.''
\bverse Thus Noah\index{Noah} did; according to all that God commanded him, so he did.
