% Chapter 24 of Genesis
\bookchapter{A Bride for \name{Isaac}}

\bverse Now \Abraham was old, well advanced in age; and the \lord had blessed \Abraham in all things.
\bverse So \Abraham said to the oldest servant of his house, who ruled over all that he had, ``Please, put your hand under my thigh,
\bverse and I will make you swear by the \lord, the God of heaven and the God of the earth, that you will not take a wife for my son from the daughters of the Canaanites, among whom I dwell;
\bverse but you shall go to my country and to my family, and take a wife for my son \name{Isaac}.
\bverse And the servant said to him, ``Perhaps the woman will not be willing to follow me to this land, Must I take your son back to the land from which you came?''
\bverse But \Abraham said to him, ``Beware that you do not take my son back there.
\bverse The \lord God of heaven, who took me from my father's house and from the land of my family, and who spoke to me and swore to me, saying, `To your descendants I give this land,' He will sent His angel before you, and you shall take a wife for my son from there.
\bverse And if the woman is not willing to follow you, then you will be released from this oath; only do not take my son back there.''
\bverse So the servant put his hand under the thigh of \Abraham his master, and swore to him concerning this matter.
\bverse Then the servant took ten of his master's camels and departed, for all his master's goods \textit{were in} his hand. And he arose and went to \location{Mesopotamia}, to the city of \location{Nahor}.
\bverse And he made his camels kneel down outside the city by a well of water at evening time, the time when women go out to draw \textit{water}.
\bverse Then he said, ``O \lord God of my master \Abraham, please give me success this day, and show kindness to my master \Abraham.
\bverse Behold, \here I stand by the well of water, and the daughters of the men of the city are coming out to draw water.
\bverse Now let it be that the young woman to whom I say, `Please let down your pitcher that I may drink,' and she says, `Drink, and I will also give your camels a drink'--\textit{let} her \textit{be the one} You have appointed for Your servant \Isaac. And by this I will know that You have shown kindness to my master.''
\bverse And it happened, before he had finished speaking, that behold, \name{Rebekah}, who was born to \name{Bethuel}, son of \name{Milcah}, the wife of \name{Nahor}, \Abraham's brother, came out with her pitcher on her shoulder.
\bverse Now the young woman \was very beautiful to behold, a virgin; no man had known her. And she went down to the well, filled her pitcher, and came up.
\bverse And the servant ran to meet her and said, ``Please let me drink a little water from your pitcher.''
\bverse So she said, ``Drink, my lord.'' Then she quickly let her pitcher down to her hand, and gave him a drink.
\bverse And when she had finished giving him a drink, she said, ``I will draw \textit{water} for your camels also, until they have finished drinking.''
\bverse Then she quickly emptied her pitcher into the trough, ran back to the well to draw \textit{water}, and drew for all his camels.
\bverse And the man, wondering at her, remained silent so as to know whether the \lord had made his journey prosperous or not.
\bverse Do it was, when the camels had finished drinking, that the man took a golden nose ring weighting half a shekel, and two bracelets for her wrists weighing ten \textit{shekels} of gold,
\bverse and said, ``Whose daughter \are you? Tell me, please, is there room \textit{in} your father's house for us to lodge?''
\bverse So she said to him, ``I \textit{am} the daughter of \name{Bethuel}, \name{Milcah}'s son, whom she bore to \name{Nahor}.''
\bverse Moreover she said to him, ``We have both straw and feed enough, and room to lodge.''
\bverse Then the man bowed down his head and worshiped the \lord.
\bverse And he said, ``Blessed \textit{be} the \lord God of my master \Abraham. who has not forsaken His mercy and His truth toward my master. As for me, being on the way, the \lord led me to the house of my master's brethren.''
\bverse So the young woman ran and told her mother's household these things.
\bverse Now \Rebekah had a brother whos name \was \name{Laban}, and \name{Laban} ran out to the man by the well.
\bverse So it came to pass, when he saw the nose ting, and the bracelets on his sister's wrists, and when he heard the words of his sister \Rebekah, saying, ``Thus the man spoke to me,'' that he went to the man. And there he stood by the camels at the well.
\bverse And he said, ``Come in, O blessed of the \lord! Why do you stand outside? For I have prepared the house, and a place for the camels.''
\bverse Then the man came to the house. And he unloaded the camels, and provided straw and feed for the camels, and water to wash his feet and the feet of the men who \were with him.
\contextnote{}{In that culture, the people were on their feet a lot more. They probably did not have boots and socks which are as covering as modern day footwear. Their feet would become dirty - especially compared to the rest of them. They would clean their feet after long journeys so that they could comfortably stay in one place. Imagine having dirty feet and trying to relax in a bed or even in a dwelling. This was a common thing to wash your feet, which is not something we think about today in many cultures where immediate access to regular showers and modern footwear is common. It has been this way for most of human history. This brings a whole new meaning to \bref{John 13:5}, when Jesus washed his disciples feet - which isn't something that is as needed in modern times.}

\bverse \textit{Food} was set before him to eat, but he said, ``I will not eat until I have told about my errand.'' And he said, ``Speak on.''
\bverse So he said, ``I \textit{am} \Abraham's servant.
\bverse The \lord has blessed my master greatly, and he has become great; and He has given him flocks and herds, silver and gold, male and female servants, and camels and donkeys.
\bverse And \Sarah my master's wife bore a son to my master when she was old; and to him he has given all that he has.
\bverse Now my master made me swear, saying, `You shall not take a wife for my son from the daughters of the \people{Canaanites}, in whose land I dwell;
\bverse but you shall go to my father's house and to my family, and take a wife for my son.'
\bverse And I said to my master, `Perhaps the woman will not follow me.'
\bverse But he said to me, `The \lord, before whom I walk, will send His angel with you and prosper your way; and you shall take a wife for my son from my family and my father's house.
\bverse You will be clear from this oath when you arrive among my family; for if they will not give \textit{her} to you, then you will be released from my oath.'
\bverse ``And this day I came to the well and said, `O \lord God of my master \Abraham. of You will now prosper the way in which I go,
\bverse behold, I stand by the well of water; and it shall come to pass that when the virgin comes out to draw \textit{water}, and I say to her, ``Please give me a little water from your pitcher to drink,''
\bverse and she says to me, ``Drink, and I will draw for your camels also,''--\textit{let} her \textit{be} the woman whom the \lord has appointed for my master's son.'
\bverse But before I had finished speaking in my heart, there was \Rebekah, coming out with her pitcher on her shoulder; and she went down to the well and drew \textit{water}. And I said to her, `Please let me drink.' 
\bverse And she made haste and let her pitcher down from her \textit{shoulder}, and said, `Drink and I will give your camels a drink also.' So I drank, and she gave the camels drink also.
\bverse Then I asked her, and said, `Whose daughter \textit{are} you?' And she said, `The daughter of \name{Bethuel}, \name{Nahor}'s son, whom \name{Milcah} bore to him.' So I put the nose ring on her nose and the bracelets on her wrists.
\bverse And I bowed my head and worshiped the \lord, and blessed the \lord God of my master \Abraham, who had led me in the way of truth to take the daughter of my master's brother for his son.
\bverse Now if you will deal kindly and truly with my master, tell me. And if not, tell me, that I may turn to the right hand or to the left.''
\bverse Then \name{Laban} and \name{Bethuel} answered and said, ``The thing comes from the \lord; we cannot speak to you either bad or good.
\bverse Here \is \Rebekah before you; take \textit{her} and go, and let her be your master's son's wife, as the \lord has spoken.''
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
