% Chapter 12 of Genesis
\bookchapter{Promises to \name{Abram}}

\bverse Now the \lord had said to \name{Abram}:
\begin{bquotation}
``Get out of your country, From your family And from your father's house, To a land that I will show you. \bverse I will make you a great nation; I will bless you And make your name great; And you shall be a blessing. \bverse I will bless those who bless you, And I will curse him who curses you; And in you all the families of the earth shall be blessed.''
\end{bquotation}

\bverse So \name{Abram} departed as the \lord had spoken to him, and \name{Lot} went with him. And \name{Abram} \was seventy-five years old when he departed from Haran.
\bverse Then \name{Abram} took \name{Sarai} his wife and \name{Lot} his brother's son, and all their possessions that they had gathered, and the people whom they had acquired in Haran, and they departed to go to the land of Canaan. So they came to the land of Canaan.
\bverse \name{Abram} passed through the land to the place of Shechem, as far as the terebinth tree of Moreh. And the Canaanites \were then in the land.
\bverse Then the \lord appeared to \name{Abram} and said, ``To your descendants I will give this land.'' And there he build an altar to the \lord, who had appeared to him.
\bverse And he moved from there to the mountain east of Bethel, and he pitched his tent \textit{with} Bethel on the west and Ai on the east; there he built an altar to the \lord and called on the name of the \lord.
\bverse So \name{Abram} journeyed, going on still toward the South.

\bmarker{Abram in Egypt}

\bverse Now there was a famine in the land, and \name{Abram} went down to Egypt to dwell there, for the famine \was severe in the land.
\bverse And it came to pass, when he was close to entering Egypt, that he said to \name{Sarai} his wife, ``Indeed I know that you \are a woman of beautiful countenance.
\bverse Therefore it will happen, when the Egyptians see you, that they will say, `This \is his wife'; and they will kill me, but they will let you live.
\bverse Please say you \are my sister, that it may be well with me for your sake, and that I may live because of you.''
\bverse So it was, when \name{Abram} came into Egypt, that the Egyptians saw the woman, that she \was very beautiful.
\bverse The princes of Pharaoh also saw her and commended her to Pharaoh. And the women was taken to Pharaoh's house.
\bverse He treated \name{Abram} well for her sake. He had sheep, oxen, male donkeys, male and female servants, female donkeys, and camels.
	\questionnote{}{Why are male and female donkey's separated here in this list? What is the significance - perhaps something culturally significant?}

\bverse But the \lord plagued Pharaoh and his house with great plagues because of \name{Sarai}, \name{Abram}'s wife.
\bverse And Pharaoh called \name{Abram} and said ``What \is this you have done to me? Why did you say `She \is my sister'? I might have taken her as my wife. Now therefore, here is your wife; take \textit{her} and go your way.''
\bverse So Pharaoh commanded \textit{his} men concerning him; and they sent him away with his wife and all that he had.