% Chapter 18 of Genesis
\bookchapter{The Son of Promise}

\bverse Then the \lord appeared to him by the terebinth trees of Mamre, as he was sitting in the tent door in the heat of the day.
\bverse So he lifted his eyes and looked, and behold, three men were standing by him; and when he saw \textit{them}, he ran from the tent door to meet them, and bower himself to the ground,
\bverse and said, ``My \lord, if I have now found favor in Your sight, do not pass on by Your servant.
\bverse Please let a little water be brought, and wash your feet, and rest yourselves under the tree.
\bverse And I will bring a morsel of bread, that you may refresh your hearts. After that you may pass by, inasmuch as you have come to your servant.'' They said, ``Do as you have said.''
\bverse So \Abraham hurried into the tent to \Sarah and said, ``Quickly, make ready three measures of fine meal; knead \textit{it} and make cakes.''
\bverse And \Abraham ran to the herd, took a tender and good calf, gave \textit{it} to a young man, and he hastened to prepare it.
\bverse So he took butter and milk and the calf which he had prepared, and set \textit{it} before them; and he stood by them under the tree as they ate. 
\bverse Then they said to him, ``Where \is \Sarah your wife?'' So he said, ``Here, in the tent.''
\bverse And He said, ``I will certainly return to you according to the time of life, and behold, \Sarah your wife shall have a son.'' (\Sarah was listening in the tent door which \was behind him.)
\bverse Now \Abraham and \Sarah were old, well advanced in age, \textit{and} \Sarah had passed the age of childbearing.
\bverse Therefore \Sarah laughed within herself\vmark{a}, saying ``After I have grown old, shall I have pleasure, my lord being old also?''
	\generalnote{a}{Does this mean she only thought it? If so, then her thoughts are being read in the following verses - which shows some of the capabilities of the \lord.}

\bverse And the \lord said to \Abraham, ``Why did \Sarah laugh, saying, `Shall I surely bear \textit{a child}, since I am old?'
\bverse Is anything too hard for the \lord? At the appointed time I will return to you, according to the time of life, and \Sarah shall have a son.''
\bverse But \Sarah denied \textit{it}, saying, ``I did not laugh,'' for she was afraid. And He said, ``No, but you did laugh!''

\bmarkerdown{\Abraham Intercedes for \location{Sodom}}

\bverse Then the men rose from there and looked toward \location{Sodom}, and \Abraham went with them to send them on the way.
\bverse And the \lord said, ``Shall I hide from \Abraham what I am doing,
\bverse since \Abraham shall surely become a great and imghty nation, and all the nations of the earth shall be blessed in him?
\bverse For I have known him, in order that he may command his children and his household after him, that they keep the way of the \lord, to do righteousness and justice, that the \lord may bring to \Abraham what He has spoken to him.''
\bverse And the \lord said, ``Because the outcry against \location{Sodom} and \location{Gomorrah} is great, and because their sin is very grave,
\bverse I will go down now and see whether they have done altogether according to the outcry against it that has come to Me; and if not, I will know.''
\bverse Then the men turned away from there and went toward \location{Sodom}, but \Abraham still stood before the \lord.
\bverse And \Abraham came near and said, ``Would You also destroy the righteous with the wicked?
\bverse Suppose there were fifty righteous within the city; would You also destroy the place and not spare \textit{it} for fifty righteous that were in it?
\bverse Far be it from You to do such a thing as this, to slay the righteous with the wicked, so that the righteous should be as the wicked; far be it from You! Shall not the Judge of all the earth do right?''
\bverse So the \lord said, ``If I find in \location{Sodom} fifty righteous within the city, then I will spare all the place for their sakes.''
\bverse Then \Abraham answered and said, ``Indeed now, I who \textit{am but} dust and ashes have taken it upon myself to speak to the \lord:
\bverse Suppose there were five less than the fifty righteous; would you destroy all of the city for \textit{lack of} five?'' He said, ``If I find there forty-five, I will not destroy \textit{it}.''
\bverse And he spoke to Him yet again and said, ``Suppose there should be forty found there?'' So He said, ``I will not do \textit{it} for the sake of forty.''
\bverse Then he said, ``Let not the Lord be angry, and I will speak: Suppose thirty shall be found there?'' So He said, ``I will not do \textit{it} if I find thirty there."
\bverse And he said, ``Indeed now, I have taken it upon myself to speak to the Lord: Suppose twenty should be found there?'' So He said, ``I will not destroy \textit{it} for the sake of twenty.''
\bverse Then he said, ``Let not the Lord be angry, and I will speak but once more: Suppose ten should be found there?'' And He said, ``I will not destroy \textit{it} for the sake of ten.''
\bverse So the \lord went His way as soon as He had finished speaking with \Abraham; and \Abraham returned to his place.
