% Chapter 19 of Genesis
\bookchapter{\location{Sodom}'s Depravity}

\bverse Now the two angels came to \location{Sodom} in the evening, and \name{Lot} was sitting in the gate of \location{Sodom}. When \name{Lot} saw \textit{them}, he rose to meet them, and he bowed himself with his face toward the ground.
\bverse And he said, ``Here now, my lords, please turn in to your servant's house and spend the night, and wash your feet; then you may rise early and go on your way.'' And they said, ``No, but we will spend the night in the open square.''
\bverse But he insisted strongly; so they turned in to him and entered his house. Then he made them a feast, and baked unleavened bread, and they ate\vmark{a}.
	\generalnote{a}{Here the angels eat food. Which humanizes them and demonstrates that they can do things that normal humans do like interacting with the physical and eating.}

\bverse Now before they lay down, the men of the city, the men of \location{Sodom}, both old and young, all the people from every quarter, surrounded the house.
\bverse And they called to \name{Lot} and said to him, ``Where are the men\vmark{a} who came to you tonight? Bring them out to us that we may know them \textit{carnally}.''
	\generalnote{a}{The townsfolk recognize these as men, despite them being angels. This further demonstrates that angels can appear as human.}
	\questionnote{}{Are there humans around us which are actually angels interacting with us? This is certainly suggested in \bref{Hebrews 13:2}.}

\bverse So \name{Lot} went out to them through the doorway, shut the door behind him, 
\bverse and said, ``Please, my brethren, do not do so wickedly! 
\bverse See now, I have two daughters who have not known a man; please, let me bring them out to you, and you may do to them as you wish; only do nothing to these men, since this is the reason they have come under the shadow of my roof.''
	\contextnote{}{Offering his two daughters to the mob is such an extreme act. This could demonstrate that \name{Lot} recognizes that the men are angels sent from God and perhaps he thinks that if the acts of the mob are carried out, that God's wrath will be sent down on them. Otherwise, why would he offer such an extreme counter offer in response?}

\bverse And they said, ``Stand back!'' Then they said, ``This one came in to stay \textit{here}, and he keeps acting as a judge; now we will deal worse with you than with them.''So they pressed hard against the man \name{Lot}, and came near to break down the door.
\bverse But the men reached out their hands and pulled \name{Lot} into the house with them, and shut the door.
\bverse And they struck the men who \were at the doorway of the house with blindness, both small and great, so that they became weary \textit{trying} to find the door.

\bmarkerdown{\location{Sodom} and \location{Gomorrah} Destroyed}

\bverse Then the men said to \name{Lot}, ``Have you anyone else here? Son-in-law, your sons, your daughters, and whomever you have in the city--take \textit{them} out of this place!
\bverse For we will destroy this place, because the outcry against them has grown great before the face of the \lord, and the \lord has sent us to destroy it.''
\bverse So \name{Lot} went out and spoke to his sons-in-law, who had married his daughters, and said, ``Get up, get out of this place; for the \lord will destroy this city!'' But to his sons-in-law he seemed to be joking.
\bverse When the morning dawned, the angels urged \name{Lot} to hurry, saying, ``Arise, take your wife and your two daughters who are here, lest you be consumed in the punishment of the city.''
\bverse And while he lingered the men took hold of his hand, his wife's hand, and the hands of his two daughters, the \lord being merciful to him, and they brought him out and set him outside the city.
\bverse So it came to pass, when they had brought them outside, that he said, ``Escape for your life! Do not look behind you nor stay anywhere in the plain. Escape to the mountains, lest you be destroyed.''
\bverse Then \name{Lot} said to them, ``Please, no, my lords!
\bverse Indeed now, your servant has found favor in your sight, and you have increased your mercy which you have shown me by saving my life; but I cannot escape to the mountains, lest some evil overtake me and I die.
\bverse See now, this city \is near \textit{enough} to flee to, and it \is a little one; please let me escape there (\is it not a little one?) and my soul shall live.''
\bverse And he said to him, ``See, I have favored you concerning this thing also, in that I will not overthrow this city for which you have spoken.
\bverse Hurry, escape there. For I cannot do anything until you arrive there.'' Therefore the name of the city was called \location{Zoar}.
\bverse The sun had risen upon the earth when \name{Lot} entered \location{Zoar}. 
\bverse Then the \lord rained brimstone and fire on \location{Sodom} and \location{Gommorah}, from the \lord out of heavens.
\bverse So He overthrew those cities, all the plain, all the inhabitants of the cities, and what grew on the ground.
\bverse But his wife looked back behind him, and she became a pillar of salt.
\bverse And \name{Abraham} went early in the morning to the place where he had stood before the \lord.
\bverse Then he looked toward \location{Sodom} and \location{Gomorrah}, and toward all the land of the plain; and he saw, and behold, the smoke of the land which went up like the smoke of a furnace.
\bverse And it came to pass, when God destroyed the cities of the plain, that God remembered \name{Abraham}, and sent \name{Lot} out of the midst of the overthrow, when He overthrew the cities in which \name{Lot} had dwelt.

\bmarkerdown{The Descendants of \name{Lot}}

\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
