% Chapter 22 of Genesis
\bookchapter{\Abraham's Faith Confirmed}

\bverse Now it came to pass after these things that God tested \Abraham, and said to him, ``\Abraham!'' And he said, ``Here I am.''
\bverse Then He said, ``Take now your son, your only \textit{son} \Isaac, whom you love, and go to the land of \location{Moriah}, and offer him there as a burnt offering on one of the mountains of which I shall tell you.''
	\questionnote{}{If God can tell your heart (\bref{Psalm 44:21}, \bref{Matthew 9:4}), why did he need \Abraham to do this physical act to confirm his faith? Perhaps this is here to show how important works are, as it states in \bref{James 2:26}.}

\bverse So \Abraham rose early in the morning and saddled his donkey, and took two of his young men with him, and \Isaac his son; and he split the wood for the burnt offering, and arose and went to the place of which God had told him.
\bverse Then on the third day \Abraham lifted his eyes and saw the place afar off.
\bverse And \Abraham said to his young men, ``Stay here with the donkey; the lad and I will go yonder and worship, and we will come back to you.''
\bverse So \Abraham took the wood of the burnt offering and laid \textit{it} on \Isaac his son; and he took the fire in his hand, and a knife, and the two of them went together.
\bverse But \Isaac spoke to \Abraham his father and said, ``My father!'' And he said, ``Here I am, my son.'' Then he said, ``Look, the fire and the wood, but where \is the lamb for a burnt offering?''
\bverse And \Abraham said, ``My son, God will provide for Himself the lamb for a burnt offering.'' So the two of them went together.
\bverse Then they came to the place of which God had told him. And \Abraham built an altar there and placed the wood in order; and he bound \Isaac his son and laid him on the altar, upon the wood.
\bverse And \Abraham stretched out his hand and took the knife to slay his son.
\bverse But the Angel of the \lord called to him from heaven and said, ``\Abraham, \Abraham!'' So he said, ``Here I am.''
\bverse And He said, ``Do not lay your hand on the lad, or do anything to him; for now I know that you fear God, since you have not withheld your son, your only \textit{son}, from Me.''
\bverse Then \Abraham lifted his eyes and looked, and there behind \textit{him was} a ram caught in a thicket by its horns. So \Abraham went and took the ram, and offered it up for a burnt offering instead of his son. 
\bverse And \Abraham called the name of the place, The-\lord-Will-Provide\index{Locations:The-LORD-Will-Provide}; as it is said \textit{to} this day, ``In the Mount of the \lord it shall be provided.''
\bverse Then the Angel of the \lord called to \Abraham a second time out of heaven,
\bverse and said: ``By Myself I have sworn, says the \lord, because you have done this thing\vmark{a}, and have not withheld your son, your only \textit{son}--
	\doctrinenote{a}{This is a strong example to show that \textit{works} are very important in demonstrating our faith (as it says in \bref{James 2:14}). Some believe that God should just know the heart of each and every one of us (which is true) and such that we do not need to perform works or \textit{actions} to show what our heart is. However, the concept of \textit{free will} makes actions necessary. God is omnipresent and exists outside of time (\bref{Genesis 1:1}). Therefore, the actions throughout our lives are likely \textit{how} he knows our heart, and therefore necessary. Despite this, we have free will, so in any moment, we can choose to go with or against our faith. In this moment, \Abraham is supporting his faith with works. The works in this case are so extreme, that they demonstrate clearly the level of faith that he has.}

\bverse blessings I will bless you, and multiplying I will multiply your descendants as the stars of the heaven and as the sand which \is on the seashore; and your descendants shall possess the gate of their enemies.
\bverse In your seed all the nations of the earth shall be blessed, because you have obeyed My voice.''
\bverse So \Abraham returned to his young men, and they rose and went together to \location{Beersheba}; and \Abraham dwelt at \location{Beersheba}.

\bmarkerdown{The Family of \name{Nahor}}

\bverse Now it came to pass after these things that it was told \Abraham, saying, ``Indeed \name{Milcah} also has borne children to your brother \name{Nahor}:
\bverse \name{Huz} his firstborn, \name{Buz} his brother, \name{Kemuel} the father of \name{Aram},
\bverse \name{Chesed}, \name{Hazo}, \name{Pildash}, \name{Jidlaph}, and \name{Bethuel}.''
\bverse And \name{Bethuel} begot \name{Rebekah}. These eight \name{Milcah} bore to \name{Nahor}, \Abraham's brother.
\bverse His concubine, whose name was \name{Reumah}, also bore \name{Tebah}, \name{Gaham}, \name{Thahash}, and \name{Maachah}.
