% Chapter 20 of Genesis
\bookchapter{\name{Abraham} and \name{Abimelech}}

\bverse And \name{Abraham} journeyed from there to the South, and dwelt between \location{Kadesh} and \location{Shur}, and stayed in \location{Gerar}.
\bverse Now \name{Abraham} said of \name{Sarah} his wife, ``She \is my sister.'' And \name{Abimelech} king of \location{Gerar} sent and took \name{Sarah}.
	\contextnote{}{Did he not learn from the past? This is the same thing that happened in \bref{Genesis 12:11}.}
	
\bverse But God came to \name{Abimelech} in a dream by night, and said to him, ``Indeed you \are a dead man because of the woman whom you have taken, for she \is a man's wife.''

	\todo{This example and that in \bref{Genesis 12:11} could make a good sermonette topic. Ignorance of the law is not an excuse to break the law. In this case, not knowing that \name{Sarah} was married is still no valid excuse for acting as though she is single.}

\bverse But \name{Abimelech} had not come near herl and he said, ``Lord, will You slay a righteous nation also?
\bverse Did he not say to me, `She \is my sister'? And she, even she herself said, `He \is my brother.' In the integrity of my heart and innocence of my hands I have done this.''
\bverse And God said to him in a dream, ``Yes, I know that you did this in the integrity of your heart. For I also withheld you from sinning against Me; therefore I did not let you touch her.
\bverse Now therefore, restore the man's wife; for he \is a prophet, and he will pray for you and you shall live. But if you do not restore \textit{her}, know that you shall surely die, you and all who \are yours.''
\bverse So \name{Abimelech} rose early in the morning, called all his servants, and told all these things in their hearing; and the man were very much afraid.
\bverse And \name{Abimelech} called \name{Abraham} and said to him, ``What have you done to us? How have I offended you, that you have brought on me and on my kingdom a great sin? You have done deeds to me that ought not to be done.''
\bverse Then \name{Abimelech} said to \name{Abraham}, ``What did you have in view, that you have done this thing?''
\bverse And \name{Abraham} said, ``Because I thought, surely the fear of God \is not in this place; and they will kill me on account of my wife.
\bverse But indeed \textit{she} is truly my sister. She \is the daughter of my father, but not the daughter of my mother; and she became my wife.
\bverse And it came to pass, when God caused me to wander from my father's house, that I said to her, `This \is your kindness that you should do for me: in every place, wherever we go, say of me, ``He \is my brother.'' ' ''
\bverse Then \name{Abimelech} took sheep, oxen, and male and female servants, and gave \textit{them} to \name{Abraham}; and he restored \name{Sarah} his wife to him.
\bverse And \name{Abimelech} said, ``See, my land \is before you; dwell where it pleases you.''
\bverse Then to \name{Sarah} he said, ``Behold, I have given your brother a thousand \textit{pieces} of silver; indeed this vindicates you before all who \are with you and before everybody.'' Thus, she was rebuked.
\bverse So \name{Abraham} prayed to God; and God healed \name{Abimelech}, his wife, and his female servants.Then they bore \textit{children};
\bverse for the \lord had closed up all the wombs of the house of \name{Abimelech} because of \name{Sarag}, \name{Abraham}'s wife.
