% Chapter 3 of Genesis
\bookchapter{The Temptation and Fall of Man}


\bverse Now the serpent\vmark{a} was more cunning than any beast of the field which the \lord God had made. And he said to the woman, ``Has God indeed said, `You shall not eat of every tree of the garden'?''
	\crossrefnote{a}{In \bref{Revelation 12:9}, the ``serpent of old'' is referred to as ``the Devil\index{Devil} and Satan\index{Satan}.'' This is well known to be this serpent here in Genesis.}

\bverse And the woman said to the serpent, ``We may eat of the fruit of the trees of the garden;
\bverse but of the fruit of the tree which \textit{is} in the midst of the garden God has said, `You shall not eat it, nor shall you touch it\vmark{a}, lest you die.' ''
	\questionnote{a}{Did God say ``not shall you touch it'' or was this added by the woman? Perhaps they added this in their minds as a \textit{safeguard} to keep them from even being tempted by the tree. For if they never touch it, they surely would fulfill never eating it.}

\bverse Then the serpent said to the woman, ``You will not surely die\vmark{a}.
	\generalnote{a}{This is the first example of a \textit{lie} within the Bible. Satan\index{Satan} uses a single word to change a truth to a lie. He then follows it up with what appears to be truth (though they may not know that) to both entice and persuade the woman that he knows things they do not - that God was not telling them the whole truth.}

\bverse For God knows\vmark{a} that in the day you eat of it, your eyes will be opened, and you will be like God, knowing good and evil\vmark{b}.''
	\generalnote{a}{This is a tactic of deception. Satan\index{Satan} is making it seem like God knows something that he may be intentionally keeping from them.}
	\doctrinenote{b}{To go against God is the definition of sin\index{Sin}, which is an evil that they will immediately know.}

\bverse So when the woman saw that the tree \textit{was} good for food, that it \textit{was} pleasant to the eyes\vmark{a}, and a tree desirable to make \textit{one} wise\vmark{b}, she took of its fruit\vmark{c}, and ate. She also gave to her husband with her\vmark{d}, and he ate.
	\contextnote{a}{When questioning the commandment to not eat the tree, the first thing the woman noticed was that this tree fit other characteristics of the trees which they were allowed to eat of.}
	\contextnote{b}{The serpents words were interpreted as a good thing for the woman. She took the information she was given and saw it as good.}
	\contextnote{c}{When she took of the fruit, she would have noticed that she did not immediately die. In \bref{Genesis 3:2}, she said she could not \textit{touch it} lest they die - which they likely added to Gods commandment. When seeing that she did not die from touching it, she could have deceived herself into thinking that they were not told what is true, which then made the decision to eat of it easier to come to.}
	\translationnote{d}{The phrase ``her husband with her'' perhaps makes it seem (at least how it appears in English) like Adam\index{Adam} was with her the entire time as this was happening or at least with her when she took of the tree.}
	

\bverse Then the eyes of both of them were opened, and they knew that they \textit{were} naked; and they sewed fig leaves together and made themselves coverings.
\bverse And they heard the sound of the \lord God walking in the garden in the cool of the day\vmark{a}, and Adam\index{Adam} and his wife hid themselves from the presence of the \lord God. among the trees of the garden.
	\contextnote{a}{This makes it seem like a regular and completely normal occurrence that God is walking around the garden with them.}

\bverse Then the \lord God called to Adam and said to him, ``Where \textit{are} you?''
\bverse So he said, ``I heard Your voice in the garden, and I was afraid because I was naked; and I hid myself.''
\bverse And He said, ``Who told you that you \textit{were} naked? Have you eaten from the tree of which I commanded you that you should not eat?''
\bverse Then the man said, ``The woman whom You gave \textit{to be} with me, she gave me of the tree, and I ate.''
\bverse And the \lord God said to the woman, ``What \textit{is} this you have done?'' The woman said, ``The serpent deceived me, and I ate.''
\bverse So the \lord God said to the serpent: 
\begin{bquotation}
``Because you have done this, You \textit{are} cursed more than all cattle, And more than every beast of the field; On your belly you shall go, And you shall eat dust All the days of your life.
\bverse And I will put enmity Between you and the woman, And between your seed and her Seed; He shall bruise your head, And you shall bruise His heel.''
\end{bquotation}
\bverse To the woman He said: 
\begin{bquotation}
``I will greatly multiply your sorrow and your conception In pain you shall bring forth children; Your desire \textit{shall be} for your husband, And he shall rule over you.''
\end{bquotation}
\bverse Then to Adam He said, ``Because you have heeded the voice of your wife\vmark{a}, and have eaten from the tree of which I commanded you, saying, `you shall not eat of it':
\begin{bquotation}
Cursed \textit{is} the ground for your sake; In toil you shall eat \textit{of} it All the days of your life.
	\doctrinenote{a}{This echos the concept that we are held personally accountable for our actions and we can not let others pressure our decisions. God \textit{gave} Adam his wife, and yet God still held Adam to a standard of responsibility for his actions.}

\bverse Both thorns and thistles it shall bring forth for you, And you shall eat the herb of the field.
\bverse In the sweat of your face you shall eat bread Till you return to the ground, For our of it you were taken; For dust you \textit{are} And to dust you shall return.''
\end{bquotation}
\bverse And Adam called his wife's name Eve, because she was the mother of all living.
	\contextnote{}{Some trains of thought argue that there were other people on earth at this time that did not come from Adam and Eve - this scripture directly disproves that.}

\bverse Also for Adam and his wife, the \lord God made tunics of skin, and clothed them.
\bverse Then the \lord God said, ``Behold, the man has become like one of Us, to know good and evil. And now, lest he put out his hand and take also of the tree of life, and eat, and live forever'' --
\bverse therefore the \lord God sent him out of the garden of Eden to till the ground from which he was taken.
\bverse So He drove out the man; and He placed cherubim at the east of the garden of Eden, and a flaming sword which turned every way, to guard the way to the tree of life.



