% Chapter 27 of Genesis
\bookchapter{\Isaac Blesses \Jacob}

\bverse Now it came to pass, when \Isaac was old and his eyes were so dim that he could not see, that he called \Esau his older son and said to him, ``My son.'' And he answered him ``Here I am.''
\bverse Then he said, ``Behold now, I am old. I do not know the day of my death.
\bverse Now therefore, please take your weapons, your quiver and your bow, and go out to the field and hunt game for me.
	\generalnote{}{This could be used to suggest that hunting is okay, which is a common thing some people argue against in our modern culture.}
 
\bverse And make me savory food, such as I love, and bring \textit{it} to me that I may eat, that my soul may bless you before I die.''
\bverse Now \Rebekah was listening when \Isaac spoke to \Esau his son. And \Esau went to the field to hunt game and to bring \textit{it}.
\bverse So \Rebekah spoke to \Jacob her son, saying, ``Indeed I heard your father speak to \Esau your brother, saying
\bverse `Bring me game and make savory food for me, that I may eat it and bless you in the presence of the \lord before my death.'
\bverse Now therefore, my son, obey my voice according to what I command you.
\bverse Go now to the flock and bring me from there two choice kids of the goats, and I will make savory food from them for your father, such as he loves.
\bverse Then you shall take \textit{it} to your father, that he may eat \textit{it}, and that he may bless you before his death.''
	\contextnote{}{Earlier, in \bref{Genesis 25:28}, it is said that \Rebekah loves \Jacob. However, it is phrased in a way which suggests she does \textit{not} love \Esau. This could be why she is trying to undermine \Isaac's wishes here. Alongside this, it fits with \bref{Genesis 25:34}, where \Esau sold his birthright to \name{Jacob}, which could be fulfilled in this scenario.}

\bverse And \Jacob said to \Rebekah his mother, ``Look, \Esau my brother \textit{is} a hairy man, and I \textit{am} a smooth-\textit{skinned} man.
\bverse Perhaps my father will feel me, and I shall seem to be a deceiver to him; and I shall bring a curse on myself and not a blessing.''
	\bverse But his mother said to him, ``\textit{Let} your curse \textit{be} on me, my son; only obey my voice, and go, get \them for me.''
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
\bverse 
