% Chapter 21 of Genesis
\bookchapter{\Isaac Is Born}

\bverse And the \lord visited \Sarah as He had said, and the \lord did for \Sarah as He had spoken.
\bverse For \Sarah conceived and bore \Abraham a son in his old age, at the set time which God had spoken to him.
\bverse And \Abraham called the name of his son who was born to him--whom \Sarah bore to him--\Isaac. 
\bverse Then \Abraham circumcised his son \Isaac when he was eight days old\vmark{a}, as God had commanded him.
	\generalnote{a}{Circumcision was to be done on the eighth day.}

\bverse Now \Abraham was one hundred years old when his son \Isaac was born to him.
\bverse And \Sarah said, ``God has made me laugh, \textit{and} all who hear will laugh with me.''
\bverse She also said, ``Who would have said to \Abraham that \Sarah would nurse children? For I have borne \textit{him} a son in his old age.''

\bmarkerdown{\name{Hagar} and \name{Ishmael} Depart}

\bverse So the child grew and was weaned. And \Abraham made a great feast on the same day that \Isaac was weaned.
\bverse And \Sarah saw the son of \name{Hagar} the \people{Egyptian}, whom she had borne to \Abraham, scoffing.
\bverse Therefore she said to \Abraham, ``Cast out this bondwomen and her son; for the son of this bondwoman shall not be heir with my son, \textit{namely} with \Isaac.''
\bverse And the matter was very displeasing in \Abraham's sight because of his son.
\bverse But God said to \Abraham, ``Do not let it be displeasing in your sight because of the lad or because of your bondwoman. Whatever \Sarah has said to you, listen to her voice; for in \Isaac your seed shall be called.
\bverse Yet I will also make a nation of the son of the bondwoman, because he \is your seed.''
\bverse So \Abraham rose early in the morning and took bread and a skin of water; and putting \textit{it} on her shoulder, he gave \textit{it} and the boy to \name{Hagar}, and sent her away. Then she departed and wandered in the Wilderness of Beersheba.
\bverse And the water in the skin was used up, and she placed the boy under one  of the shrubs.
\bverse Then she went and say down across from \textit{him} at a distance of about a bowshot; for she said to herself, ``Let me not see the death of the boy.'' So she sat opposite \textit{him}, and lifted her voice and wept.
\bverse And God heard the voice of the lad. Then the angel of God called to \name{Hagar} out of heaven, and said to her, ``What ails you, \name{Hagar}? Fear not, for God has heard the voice of the lad where he \is. 
\bverse Arise, lift up the lad and hold him with your hand, for I will make him a great nation.''
\bverse Then God opened her eyes, and she saw a well of water. And she went and filled the skin with water, and gave the lad a drink.
\bverse So God was with the lad; and he grew and dwelt in the wilderness, and became an archer.
\bverse He dwelt in the Wilderness of \location{Paran}; and his mother took a wife for him from the land of \Egypt. 

\bmarkerdown{A Covenant with \name{Abimelech}}

\bverse And it came to pass at that tie that \name{Abimelech} and \name{Phichol}, the commander of his army, spoke to \Abraham, saying, ``God \is with you in all that you do.
\bverse Now therefore, swear to me by God that you will not deal falsely with me, with my offspring, or with my posterity; but that according to the kindness that I have done to you, you will do to me and to the land in which you have dwelt.''
\bverse And \Abraham said, ``I will swear.''
\bverse Then \Abraham rebuked \name{Abimelech} because of a well of water which \name{Abimelech}'s servants had seized.
\bverse And \name{Abimelech} said, ``I do not know who has done this thing; you did not tell me, nor had I heard \textit{of it} until today.''
\bverse So \Abraham took sheep and oxen and gave them to \name{Abimelech}, and the two of them made a covenant.
\bverse And \Abraham set seven ewe lambs of the flock by themselves.
\bverse Then \name{Abimelech} asked \Abraham, ``What \textit{is the meaning of} these seven ewe lambs which you have set by themselves?''
\bverse And he said, ``You will take \textit{these} seven ewe lambs from my hand, that they may be my witness that I have dug this well.''
\bverse Therefore he called that place \location{Beersheba}, because the two of them swore an oath there.
\bverse Thus they made a covenant at \location{Beersheba}.  So \name{Abimelech} rose with \name{Phichol}, the commander of his army, and they returned to the land of the \people{Philistines}.
\bverse Then \textit{\Abraham} planted a tamarisk tree in \location{Beersheba}, and there called on the name of the \lord, the everlasting God.
\bverse And \Abraham stayed in the land of the \people{Philistines} many days.
