% Chapter 17 of Genesis
\bookchapter{The Sign of the Covenant}

\bverse When \name{Abram} was ninety-nine years old, the \lord appeared to \name{Abram} and said to him, ``I \textit{am} Almighty God; walk before Me and be blameless.
\bverse And I will make My covenant between Me and you, and will multiply you exceedingly.''
\bverse Then \name{Abram} fell on his face, and God talked with him, saying: 
\bverse ``As for Me, behold, My covenant is with you, and you shall be a father of many nations.
\bverse No longer shall your name be called \name{Abram}, but your name shall be \name{Abraham}; for I have made you a father of many nations.
\bverse I will make you exceedingly fruitful; and I will make nations of you, and kings shall come from you.
\bverse And I will establish My covenant between Me and you and your descendants after you in their generations, for an everlasting covenant, to be God to you and your descendants after you.
\bverse Also I give to you and your descendants after you the  land in which you are a stranger, all the land of \location{Canaan}, as an everlasting possession; and I will be their God.''
\bverse And God said to \name{Abraham}: ``As for you, you shall keep My covenant, you and your descendants after you throughout their generations.
\bverse This \is My covenant which you shall keep, between Me and you and your descendants after you: Every male child among you shall be circumcised\vmark{a};
	\questionnote{a}{Was circumcision something that existed before this point? If so, who had discovered it and for what purpose would they have done this? This is perhaps something which is \textit{strange} to have been discovered and practiced on its own without some purpose. It could make sense that this type of thing was taught to them by God, in which case it demonstrates a form of knowledge passed down from God which isn't something we would have figured out on our own.}

\bverse and you shall be circumcised in the flesh of your foreskins, and it shall be a sign of the covenant between Me and you.
\bverse He who is eight days old\vmark{a} among you shall be circumcised, every male child in your generations, he who is born in your house or bought\vmark{b} with money from any foreigner who is not your descendant.
	\questionnote{a}{What is the significance of eight days old here? In modern society, this is often ignored - but there is likely a good reason for it. What has for-sure occurred by eight days of childhood development?}
	\contextnote{b}{Buying children (perhaps a form of adoption) seems to be a common (or at least common enough to mention) practice back in these days.}

\bverse He who is born in your house and he who is bought with your money\vmark{a} must be circumcised, and My covenant shall be in your flesh for an everlasting covenant.
	\contextnote{a}{This (in a way) introduces the concept of adoption and how the covenant extends to the adopted family as well. This shows that the covenant is not with only an absolute physical bloodline, but extends to others who are adopted into the family.}	

\bverse And the uncircumcised male child, who is not circumcised in the flesh of his foreskin, that person shall be cut off from his people; he has broken my covenant.''
	\contextnote{}{This is a physical sign of being part of God's covenant. It is clear that those without this physical differentiating mark (circumcision of the foreskin) is \textit{not} part of the covenant.}

\bverse Then God said to \name{Abraham}, ``As for \name{Sarai} your wife, you shall not call her name \name{Sarai}, but \name{Sarah} \textit{shall be} her name.
\bverse And I will bless her and also give you a son by herl then I will bless her, and she shall be \textit{a mother} of nations; kings of peoples shall be from her.''
\bverse then \name{Abraham} fell on his face and laughed, and said in his heart, ``Shall \textit{a child} be born to a man who is one hundred years old? And shall \name{Sarah}, who is ninety years old, bear \textit{a child}?''
	\contextnote{}{Even though they lived much longer back then, this is around the time where the lifespans of the people were dropping significantly (see Figure \ref{fig:pre_adam_lifespans}). By this point, it is considered silly for parents of this age to be able to bear children.}

\bverse And \name{Abraham} said to God, ``Oh, that \name{Ishmael} might live before You!''
\bverse Then God said: ``No, \name{Sarah} your wife shall bear you a son, and you shall call his name \name{Isaac}; I will establish My covenant with him for an everlasting covenant, \textit{and} with his descendants after him.
\bverse And as for \name{Ishmael}, I have heard you. Behold, I have blessed him, and will make him fruitful, and will multiply him exceedingly. He shall beget twelve princes, and I will make him a great nation.
\bverse But My covenant I will establish with \name{Isaac}, whom \name{Sarah} shall bear to you at this set time next year.''
\bverse Then He finished talking with him, and God went up from Abraham.
\bverse So \name{Abraham} took \name{Ishmael} his son, all who were born in his house and all who were bought with his money, every male among the men of \name{Abraham}'s house, and circumcised the flesh of their foreskins that very same day, as God had said to him.
\bverse \name{Abraham} \was ninety-nine years old when he was circumcised in the flesh of his foreskin.
\bverse And \name{Ishmael} his son \was thirteen years old when he was circumcised in the flesh of his foreskin.
\bverse That very same day, \name{Abraham} was circumcised, and his son \name{Ishmael};
\bverse and all the men of his house, born in the house or brought with money from a foreigner, were circumcised with him.
