% Chapter 13 of Genesis
\bookchapter{\name{Abram} Inherits Canaan}

\bverse Then \name{Abram} went up from Egypt, he and his wife and all that he had, and \name{Lot} with him, to the South.
\bverse \name{Abram} \was very rich in livestock, in silver, and in gold.
\bverse And he went on his journey from the South as far as Bethel, to the place where his tent had been at the beginning, between Bethel and Ai, 
\bverse to the place of the altar which he had made there at first. And there \name{Abram} called on the name of the \lord.
\bverse \name{Lot} also, who went with \name{Abram}, had flocks and herds and tents.
\bverse Now the land was not able to support them, that they might dwell together, for their possessions were so great that they could not dwell together.
\bverse And there was strife between the herdsmen of \name{Abram}'s livestock and the herdsmen of \name{Lot}'s livestock. The Canaanites and the Perizzites then dwelt in the land.
\bverse So \name{Abram} said to \name{Lot}, ``Please let there be no strife between you and me, and between my herdsmen and your herdsmen; for we \are brethren.
	\contextnote{}{\name{Abram} was born way before the death of any of his post-flood ancestors (see figure \ref{fig:shems_genealogy}). Therefore, he likely heard stories of what strife causes and knew very well that it led to no good. Here is trying to make sure that strife does not cause division between him, \name{Lot}, and the others around them.}

\bverse Is not the whole land before you? Please separate from me. If \textit{you take} the left, then I will go to the right; or, if \textit{you go} to the right, then I will go to the left.''
	\generalnote{}{This is a perfect example of coming up with a compromise which is to avoid the strife between them, while showing that \name{Lot} can choose whichever direction he wants and \name{Abram} will be happier with the second choice rather than the strife between them.}
	
\addsermon{This example of making a compromise to avoid strife (\bref{Genesis 13:6} to \bref{Genesis 13:9}) would make a good sermonette example.}

\bverse And \name{Lot} lifted his eyes and saw all the plain of Jordan, that it \was well watered everywhere (before the \lord destroyed Sodom and Gomorrah) like the garden of the \lord, like the land of Egypt as you go toward Zoar.
\bverse Then \name{Lot} chose for himself all the plain of Jordan, and \name{Lot} journeyed east. And they separated from each other.
\bverse \name{Abram} dwelt in the land of Canaan, and \name{Lot} dwelt in the cities of the plan and pitched \textit{his} tent even as far as Sodom.
\bverse But the men of Sodom \were exceedingly wicked and sinful against the \lord.
\bverse And the \lord said to \name{Abram}, after \name{Lot} had separated from him: ``Lift your eyes now and look from the place where you are--northward, southward, eastward, and westward;
\bverse for all the land which you see I give to you and your descendants forever.
	\questionnote{}{How does this relate to this area in the modern day? Could this only be referring to the physical descendants, and so the bloodline and direct descendants still dwell in these areas - rather than the spiritual descendants (i.e., the church which is a spiritual body)? See \bref{Galatians 3:29}, and \bref{Romans 9:6} - \bref{Romans 9:8}. It's clear from the new testament that not all of the spiritual descendants live in this land.}

\bverse And I will make your descendants as the dust of the earth; so that if a man cold number the dust of the earth, \textit{then} your descendants also could be numbered.
\bverse Arise, walk in the land through its length and its width, for I give it to you.''
\bverse Then \name{Abram} moved \textit{his} tent, and went and dwelt by the terebinth trees of Mamre, which \are in Hebron, and built an altar to the \lord.
