% Chapter 23 of Genesis
\bookchapter{\Sarah's Death and Burial}

\bverse \Sarah lived one hundred and twenty-seven years; \textit{these were} the years of the life of \Sarah.
\bverse So \Sarah died in \location{Kirjath Arba} (that \textit{is}, \location{Hebron}) in the land of \location{Canaan}, and \Abraham came to mourn for \Sarah and to weep for her.
\bverse Then \Abraham stood up from before his dead, and spoke to the sons of \name{Heth}, saying
\bverse ``I \textit{am} a foreigner and a visitor among you. Give me property or a burial place among you, that I may bury my dead out of my sight.''
\bverse And the sons of \name{Heth} answered \Abraham, saying to him, 
\bverse ``Hear us, my lord: You \are a mighty prince among us; bury your dead in the choicest of our burial places. None of us will withhold from you his burial place, that you may bury your dead.''
\bverse Then \Abraham stood up and bowed himself to the people of the land, the sons of \name{Heth}.
\bverse And he spoke with them, saying, ``If it is your wish that I bury my dead out of my sight, hear me, and meet with \name{Ephron} the son of \name{Zohar} for me,
\bverse that he may give me the cave of \name{Machpelah} which he has, which \textit{is} at the end of his field. Let him give it to me at the full price, as property for a burial place among you.''
\bverse Now \name{Ephron} dwelt among the sons of \name{Heth}; and \name{Ephron} the \people{Hittite} answered \Abraham in the presence of the sons of \name{Heth}, all who entered at the gate of his city, saying,
\bverse ``No, my lord, hear me: I give you the field and the cave that \textit{is} in it; I give it to you in the presence of the sons of my people. I give it to you. Bury your dead!''
\bverse Then \Abraham bowed himself down before the people of the land;
\bverse and he spoke to \name{Ephron} in the hearing of the people of the land, saying, ``If you \text{will give it}, please hear me. I will give you money for the field; take \textit{it} from me and I will bury me dead there.''
\bverse And \name{Ephron} answered \Abraham, saying to him,
\bverse ``My lord, listen to me; the land \textit{is worth} four hundred shekels of silver. What \textit{is} that between you and me? So bury your dead.''
\bverse And \Abraham listened to \name{Ephron}; and \Abraham weighed out the silver for \name{Ephron} which he had named in the hearing of the sons of \name{Heth}, four hundred shekels of silver, currency of the merchants.
\bverse So the field of \name{Ephron} which \was in \location{Machpelah}, which \was before \location{Mamre}, the field and the cave which \was in it, and all the trees that \were in the field, which \were within all the surrounding borders, were deeded 
\bverse to \Abraham as a possession in the presence of the sons of \name{Heth}, before all who went in at the gate of his city.
\bverse And after this, \Abraham buried \Sarah his wife in the cave of the field of \location{Machpelah}, before \location{Mamre} (that is, \location{Hebron}) in the land of \location{Canaan}.
\bverse So the field and the cave that \is in it were deeded to \Abraham by the sons of \name{Heth} as property for a burial place.
