% Chapter 14 of Genesis
\bookchapter{\name{Lot}'s Captivity and Rescue}

\bverse And it came to pass in the days of \name{Amraphel} king of \location{Shinar}, \name{Arioch} king of \location{Ellasar}, \name{Chedorlaomer} king of \location{Elam}, and \name{Tidal} king of nations, 
\bverse \that they made war with \name{Bera} king of \location{Sodom}, \name{Birsha} king of \location{Gomorrah}, \name{Shinab} king of \location{Admah}, \name{Shemeber} king of Zeboiim, and the king of \location{Bela} (that is, \name{Zoar}).
\bverse All these joined together in the \location{Valley of Siddim} (that is, the Salt Sea).
\bverse Twelve years they served \name{Chedorlaomer}, and in the thirteenth year they rebelled.
\bverse In the fourteenth year, \name{Chedorlaomer} and the kings that \were with him came and attacked the Rephaim in Ashteroth Karnaim, the Zuzim in Ham, the Emim in Shaveh Kiriathaim,
\bverse and the Horites in their mountain of Seir, as far as El Paran, which \is by the wilderness.
\bverse Then they turned back adn came to En Mishpat (that \is, Kadesh), and attacked all the country of the Amalekites, and also the Amorites who dwelt in Hazezon Tamar.

\todo{Try to make sense of all these people, places, peoples, and what is going on - perhaps try drawing some diagrams?}

\todo{Create a LaTeX type to differentiate peoples (e.g., Amorites, Amalekites, etc) and locations (e.g., \location{Sodom}, \location{Elam}, etc) and have those separated into categories in the generated index.}

\bverse And the king of \location{Sodom}, the king of \location{Gomorrah}, the king of \location{Admah}, the kings of Zeboiim, and the king of \location{Bela} (that \is, \name{Zoar}) went out and joined together in battle in the \location{Valley of Siddim}
\bverse against \name{Chedorlaomer} king of \location{Elam}, \name{Tidal} king of nations, \name{Amraphel} king of \location{Shinar}, and \name{Arioch} king of \location{Ellasar}--four kings against five.
\bverse Now the \location{Valley of Siddim} \textit{was full of} asphalt pits; and the kings of \location{Sodom} and \location{Gomorrah} fled; \textit{some} fell there, and the remainder fled to the mountains.
\bverse Then they took all the goods of \location{Sodom} and \location{Gomorrah}, and all their provisions, and went their way.
\bverse They also took \name{Lot}, \name{Abram};s brother's son who dwelt in \location{Sodom}, and his goods, and departed.
\bverse Then one who had escaped came and told \name{Abram} the Hebrew, for he dwelt by the terebinth trees of \name{Mamre} the Amorite, brother of \name{Eshcol} and brother of \name{Aner}; and they \were allies with \name{Abram}.
\bverse Now when \name{Abram} heard that his brother was taken captive, he armed his three hundred and eighteen trained \textit{servants} who were born in his own house, and went in pursuit as far as Dan.
\bverse He divided his forces against them by night, and he and his servants attacked them and pursued them as far as Hobah, which \is north of \location{Damascus}.
\bverse So he brought back all the goods, and also brought back his brother \name{Lot} and his goods, as well as the women and the people.
\bverse And the king of \location{Sodom} went out to meet him at the Valley of Shaveh (that \is, the King's Valley), after his return from the defeat of \name{Chedorlaomer} and the kings who \were with him.

\bmarkerdown{\name{Abram} and \name{Melchizedek}}

\bverse Then \name{Melchizedek} king of \location{Salem} brought out bread and wine; he \was the priest of God Most High\vmark{a}.
	\translationnote{a}{This is the first time the term `Most High' has appeared. This term comes from the Hebrew term `elyown' (Strong's 5945 \cite{Hebrew Concordance}), which is an elevating title meaning \textit{the Supreme} or the \textit{Uppermost}. This is a differentiating statement which means this is referring to the literal \textit{highest} being above all others.}
	\doctrinenote{a}{This is a supporting concept to their being multiple members of the `God' family, or multiple `God' beings. This aligns with the plurality used in \bref{Genesis 1:26}, \bref{John 1:1}, \bref{John 17:5} and other places and perhaps points to the idea of a hierarchy in the God family.}

\bverse And he blessed him and said:
\begin{bquotation}
``Blessed be Abram of God Most High, Possessor of heaven and earth; \bverse And blessed be God Most High, Who has delivered your enemies into your hand.''
\end{bquotation}
And he gave him a tithe of all.
\bverse Now the king of \location{Sodom} said to \name{Abram}, ``Give me the persons, and take the goods for yourself.''
\bverse But \name{Abram} said to the king of \location{Sodom}, ``I have raised my hand to the \lord, God Most High, the Possessor of heaven and earth,
\bverse that I \textit{will take} nothing, from a thread to a sandal strap, and that I will not take anything that \is yours, lest you should say, `I have made \name{Abram} rich'--
\bverse except only what the young men have eaten, and the portion of the man who went with me: \name{Aner}, \name{Eshcol}, and \name{Mamre}; let them take their portion.''
