% Chapter 7 of Genesis
\bookchapter{The Great Flood}

\bverse Then the \lord said to \name{Noah}, ``Come into the ark\index{Ark}, you and all your household, because I have seen \that you are righteous before Me in this generation.
\bverse You shall take with you seven each of every clean animal, a male and his female; two each of animals that \are unclean, a male and his female;
\bverse also seven each of birds of the air, make and female, to keep the species alive on the face of all the earth\index{Earth}.
\bverse For after seven more days I will cause it to rain on the earth\index{Earth} forty days and forty nights, and I will destroy from the face of the earth\index{Earth} all living things that I have made.''
\bverse And \name{Noah} did according to all that the \lord commanded him.
\bverse \name{Noah} \was six hundred years old when the floodwaters were on the earth\index{Earth}.
	\timelinenote{}{\name{Noah} being six hundred would put this at year 1656 (see Figure \ref{fig:adams_genealogy}).}

\bverse So \name{Noah}, with his sons, his wife, and his sons' wives, went into the ark\index{Ark} because of the waters\index{Water} of the flood.
\bverse Of clean animals, of animals that \are unclean, of birds, and of everything that creeps on the earth\index{Earth},
\bverse two by two they went into the ark\index{Ark} to \name{Noah}, male and female, as God had commanded \name{Noah}.
\bverse And it came to pass after seven days that the waters\index{Water} of the flood were on the earth\index{Earth}.
\bverse In the six hundredth year of \name{Noah}'s life, in the second month, the seventeenth day of the month\vmark{a}, on that day all the fountains of the great deep were broken up\vmark{b}, and the windows of heaven\index{Heaven} were opened.
	\questionnote{a}{This date is \textit{very} specific. Is there any significance (other than the obvious contextual happenings) of this date?}
	\contextnote{b}{This phrase, `fountains of the great deep were broken up,' make it seem like torrential water\index{Water} came from within the earth\index{Earth}. This would sense with the context of all living things on earth\index{Earth} being destroyed in the flood - as opposed to it just being rain.}

\bverse And the rain was on the earth\index{Earth} forty days and forty nights.
\bverse On the very same day \name{Noah} and \name{Noah}'s sons, \name{Shem}, \name{Ham}, and \name{Japheth}, and \name{Noah}'s wife and the three wives of his sons with them, entered the ark\index{Ark}--
\bverse they and every beast after its kind, all cattle after their kind, every creeping thing that creeps on teh earth\index{Earth} after its kind, and every bird after its kind, every bird of every sort.
\bverse And they went into the ark\index{Ark} to \name{Noah}, two by two, of all flesh in which \textit{is} the breath\index{Breath} of life.
\bverse So those that entered, male and female of all flesh, went in as God had commanded him; and the \lord shut him in.
\bverse Now the flood was on the earth\index{Earth} forty days. The waters\index{Water} increased and lifted up the ark\index{Ark}, and it rose high above the earth\index{Earth}.
\bverse The waters\index{Water} prevailed and greatly increase on the earth\index{Earth}, and the ark\index{Ark} moved about on the surface of the waters\index{Water}.
\bverse And the waters\index{Water} prevailed exceedingly on the earth\index{Earth}, and all the high hills under the whole heaven\index{Heaven} were covered.
\bverse The waters\index{Water} prevailed fifteen cubits upward, and the mountains were covered.
\bverse And all flesh died tht moved on the earth\index{Earth}: birds and cattle and beasts and every creeping thing that creeps on the earth\index{Earth}, and every man.
\bverse All in whose nostrils \was the breath\index{Breath} of the spirit of life, all that \was on the dry \textit{land}, died.
\bverse So He destroyed all living things which were on the face of the ground: both man and cattle, creeping thing and bird of the air. They were destroyed from the earth\index{Earth}. Only \name{Noah} and those who \were with him in the ark\index{Ark} remained \textit{alive}.
\bverse And the waters\index{Water} prevailed on the earth\index{Earth} one hundred and fifty days.


\todo{Add a chart of pre-flood lifespans with birth/death year.}

