% Chapter 26 of Genesis
\bookchapter{\Isaac and \Abimelech}

\bverse There was a famine in the land, besides the first famine that was in the days of \Abraham. And \Isaac went to \Abimelech king of the \people{Philistines}, in \location{Gerar}. 
\bverse Then the \lord appeared to him and said: ``Do not go down to \location{Egypt}; live in the land of which I shall tell you.
\bverse Dwell in this land, and I will be with you and bless you; for to you and your descendants I give all these lands, and I will perform the oath which I swore to \Abraham your father.
\bverse And I will make your descendants multiply as the stars of heaven; I will give to your descendants all these lands; and in your seed all the nations of the earth shall be blessed;
\bverse because \Abraham obeyed My voice and kept My charge, My commandments, My statutes, and My laws.''

\addsermon{This (\bref{Genesis 26:5}) shows what we humans need to  do in order to have favor with God. He clearly says that he will bless his descendants and gives the \textit{why} very clearly. Through our actions, we show our character, and these actions are necessary. If \Abraham had not done these actions, this reason God stated would not have been fulfilled. This could serve as a good example for a sermonette.}

\bverse So \Isaac dwelt in \location{Gerar}.
\bverse And the men of the place asked about his wife. And he said ``She \is my sister''\vmark{a}; for he was afraid to say, ``\textit{She is} my wife,'' \textit{because he though}, ``lest the men of the place kill me for \Rebekah, because she \is beautiful to behold.''

\generalnote{a}{This mirrors the exact thing that \Abraham did with \Sarah in \bref{Genesis 20:2}.}


\addsermon{This (\bref{Genesis 26:7}) kicks off a very similar account of what happened to \Abraham with \Sarah. What is the significance? It could be a perfect example of why you should share your mistakes with your children, so that they do not make the same mistakes.}

\bverse Now it came to pass, when he had been there a long time, that \Abimelech king of the \people{Philistines} looked through a window, and saw, and there was \Isaac, showing endearment to \Rebekah his wife.
\bverse Then \Abimelech called \Isaac and said, ``Quite obviously she \is your wife; so how could you say, `She \is my sister'?'' \Isaac said to him, ``Because I said, `Lest I die on account of her.'\thinspace''
\bverse And \Abimelech said, ``What \is this you have done to us? One of the people might soon have lain with your wife, and you would have brought guilt on us.''
\bverse So \Abimelech charged all \textit{his} people, saying, ``He who touches this man or his wife shall surely be put to death.''

\contextnote{}{\Abimelech has already been through this once (\bref{Genesis 20}). He knows personally that God does not look kindly on messing with another man's wife. Therefore, he puts this warning for all the people who may not be aware of the dangers.}

\addsermon{This adds context to two of the ten commandments (\bref{Exodus 20:15} and \bref{Exodus 20:17}) by demonstrating just how serious of an offense this is. God does \textit{not} look kindly on men who would touch another man's wife - even unknowingly. This can be expanded upon quite a bit.}

\bverse Then \Isaac sowed in that land, and reaped in the same year a hundredfold; and the \lord blessed him.
\bverse The man began to prosper, and continued prospering until he became very prosperous;
\bverse for he had possessions of flocks and possessions of herds and a great number of servants. So the \people{Philistines} envied him.
\bverse Now the \people{Philistines} had stopped up all the wells which his father's servants had dug in the days of \Abraham his father, and they had filled them with earth.
\bverse And \Abimelech said to \Isaac, ``Go away from us, for you are much mightier than we.''
\bverse Then \Isaac departed from there and pitched a tent in the \location{Valley of Gerar}, and dwelt there.
\bverse And \Isaac dug again the wells of water which they had dug in the days of \Abraham his father, for the \people{Philistines} had stopped them up after the death of \Abraham. He called them by the names which his father had called them.
\bverse Also \Isaac's servants dug in the valley, and found a well of running water there.
\bverse But the herdsmen of \location{Gerar} quarreled with \Isaac's herdsmen, saying, ``The water \is ours.'' So he called the name of the well Esek, because they quarreled with him.
\bverse Then they dug another well, and they quarreled over that \textit{one} also. So he called its name \location{Sitnah}.
\bverse And he moved from there and dug another well, and they did not quarrel over it. So he called its name \location{Rehoboth}, because he said, ``For now the \lord has made room for us, and we shall be fruitful in the land.''
\bverse Then he went up from there to \location{Beersheba}.
\bverse And the \lord appeared to him the same night and said, ``I \textit{am} the God of your father \Abraham; do not fear, for I \textit{am} with you. I will bless you and multiply your descendants for My servant \Abraham's sake.''
\bverse So he built an altar there and called on the name of the \lord, and he pitched his tent there; and there \Isaac's servants dug a well.
\bverse Then \name{Abimelech} came to him from \location{Gerar} with \name{Ahuzzath}, one of his friends, and \name{Phichol} the commander of his army.
\bverse And \Isaac said to them, ``Why have you come to me, since you hate me and have sent me away from you?''
\bverse But they said, ``We have certainly seen that the \lord is with you. So we said, `Let there be an oath between us, between you and us; and let us make a covenant with you,
\bverse that you will do us no harm, since we have not touched you, and since we have done nothing to you but good and have sent you away in peace. You \are now the blessed of the \lord.'\thinspace''
\bverse So he made them a feast, and they ate and drank.
\bverse Then they arose early in the morning and swore an oath with one another; and \Isaac sent them away, and they departed from him in peace.
\bverse It came to pass the same day that \Isaac's servants came and told him about the well which they had dug, and said to him, ``We have found water.''
\bverse So he called it \location{Shebah}. Therefore the name of the city \textit{is} \location{Beersheba} to this day.
\bverse When \Esau was forty years old, he took as wives \name{Judith} the daughter of \name{Beeri} the \people{Hittite}, and \name{Basemath} the daughter of \name{Elon} the \people{Hittite}.
\bverse And they were a grief of mind to \Isaac and \Rebekah.
