% Chapter 9 of Genesis
\bookchapter{God's Promise to Noah\index{Noah}}

\bverse So God blessed Noah and his sons, and said to them: ``Be fruitful and multiply\vmark{a}, and fill the earth.
	\doctrinenote{a}{This is the same thing God told Adam and Eve in \bref{Genesis 1:28}. It is a commandment in a sense where God says to do this, which continually comes up in reference to those who follow God's ways.}

\bverse And the fear of you and the dread of you shall be on every beast of the earth, on every bird of the air, on all that move \textit{on} the earth, and on all the fish of the sea. They are given into your hand.
\bverse Every moving thing that lives shall be food for you\vmark{a}. I have given you all things, even as the green herbs.
	\questionnote{a}{This scripture (as read) make it seem like anything/all living things on earth are good for food. He is speaking here to Noah and his sons. How does this reconcile with \bref{Deuteronomy 14} (the food laws)?}

\bverse But you shall not eat flesh with its life, \textit{that is}, its blood.
	\doctrinenote{}{This makes it clear that you are NOT to eat the blood of animals.}

\bverse Surely for your lifeblood I will demand \textit{a reckoning}; from the hand of every beast I will require it, and from the hand of man. From the hand of every man's brother I will require the life of man.
\begin{bquotation}
\bverse Whoever sheds man's blood, By man his blood shall be shed; For in the image of God He made man. 
\bverse And as for you, be fruitful and multiply; Bring forth abundantly in the earth And multiply in it.''
\end{bquotation}
\bverse Then God spoke to Noah and to his sons with him, saying:
\bverse ``And as for Me, behold, I establish My covenant with you and with your descendants after you,
\bverse and with every living creature that \textit{is} with you: the birds, the cattle, and every beast of the earth with you, of all that go our of the ark, every beast of the earth.
\bverse Thus I establish My covenant with you: Never again shall all flesh be cut off by the waters of the flood; never again shall there be a flood to destroy the earth.
\bverse And God said: ``This \textit{is} the sign of the covenant which I make between Me and you, and every living creature that \textit{is} with you, for perpetual generations:
\bverse I set My rainbow in the cloud, and it shall be for the sign of the covenant between Me and the earth.
\bverse It shall be, when I bring a cloud over the earth, that the rainbow shall be seen in the cloud;
\bverse and I will remember My covenant which \textit{is} between Me and you and every living creature of all flesh; the waters shall never again become a flood to destroy all flesh.
\bverse The rainbow shall be in the cloud, and I will look on it to remember the everlasting covenant between God and every living creature of all flesh that \textit{is} on the earth.''
\bverse And God said to Noah, ``This \textit{is} the sign of the covenant which I have established between Me and all flesh that is on the earth.''

\bmarkerdown{Noah and His Sons}

\bverse Now the sons of Noah who went out of the ark were Shem, Ham, and Japheth. And Ham \was the father of Canaan\vmark{a}.
	\translationnote{a}{The word/name for `Canaan' here (Strong's 3667 \cite{Strong's GodRules}) means `lowland'.}

\bverse These three \text{were} the sons of Noah, and from these the whole earth was populated.
\bverse And Noah began \textit{to be} a farmer, and he planted a vineyard.
\bverse Then he drank of the wine and was drunk, and became uncovered in his tent.
\bverse And Ham, the father of Canaan, saw the nakedness of his father\vmark{a}, and told his two brothers outside.
	\contextnote{a}{Some speculate that much more than Ham simply seeing his father naked occurred here - such as homosexual acts. However, it does not say more than `saw the nakedness' and `told his two brothers'. It could be that in the culture of the time, this was significantly more dishonorable or shameful than it is in our modern culture, which would explain the followup curse.}

\bverse But Shem and Japheth took a garment, laid \textit{it} on both their shoulders, and went backward and covered the nakedness of their father. Their faces \were turned away, and they did not see their father's nakedness.
\bverse So Noah awoke from his wine, and knew what his younger son had done to him.
\bverse Then he said:
\begin{bquotation}
``Cursed \textit{be} Canaan; A servant of servants He shall be to his brethren.''
\end{bquotation}
\bverse And he said:
\begin{bquotation}
``Blessed \textit{be} the \lord, The God of Shem, And may Canaan be his servant.
\bverse May God enlarge Japheth, And may he dwell in the tents of Shem; And may Canaan be his servant.''
\end{bquotation}

\bverse And Noah lived after the flood three hundred and fifty years.
\bverse So all the days of Noah were nine hundred and fifty years; and he died.
	\timelinenote{}{At the time of Noah's death, 2006 years have passed since the creation of Adam (see figure \ref{fig:adams_genealogy}).}
