% Chapter 15 of Genesis
\bookchapter{God's Covenant with \name{Abram}}

\bverse After these things the word of the \lord came to \name{Abram} in a vision, saying, ``Do not be afraid, \name{Abram}. I \textit{am} your shield, your exceedingly great reward.''
\bverse But \name{Abram} said, ``Lord \god\unskip\vmark{a}, what will You give me, seeing I go childless, and the heir of my house \is \name{Eliezer} of \location{Damascus}?''
	\translationnote{a}{This is a somewhat different representation of the translation. Instead of the usual `\lord' used for God's proper name, the `Lord' here is the Hebrew word `Adonay' (Strong's 136 \cite{Hebrew Concordance}) which literally means \textit{lord} or \textit{master}, whereas the `\god' is God's proper name, which usually appears as `\lord'. So another way to write this could be `lord \lord', but that is a little weird in English.}

\bverse But \name{Abram} said, ``Look, You have given me no offspring; indeed one born in my house is my heir!''
\bverse And behold, the word of the \lord \textit{came} to him, saying, ``This one shall not be your heir, but one who will come from your own body shall be your heir.'' 
\bverse Then He brought him outside and said, ``Look, now toward heaven, and count the stars if you are able to number them.'' And He said to him, ``So shall your descendants be.''
\bverse And he believed in the \lord, and He accounted it to him for righteousness.
\bverse Then He said to him, ``I \textit{am} the \lord, who brought you out of \location{Ur} of the \people{Chaldeans}, to give you this land to inherit it.''
\bverse And he said, ``Lord \god, how shall I know that I will inherit it?''
\bverse So He said to him, ``Bring Me a three-year-old heifer, a three-year-old female goat, a three-year-old ram, a turtledove, and a young pigeon.''
\bverse Then he brought all these to Him and cut them in two, down the middle, and placed each piece opposite the other; but he did not cut the birds in two.
	\questionnote{}{Is there some sort of symbolism here with cutting the animals in half and then \textit{not} cutting the birds?}

\bverse And when the vultures came down on the carcasses, \name{Abram} drove them away.
\bverse Now when the sun was going down, a deep sleep fell upon \name{Abram}; and behold, horror \textit{and} great darkness fell upon him. 
\bverse Then He said to \name{Abram}: ``Know certainly that your descendants will be strangers in a land \textit{that is} not theirs, and will serve them, and they will afflict them four hundred years.
	\contextnote{}{This is referring to the slavery in \Egypt, where his descendants will be slaves and eventually freed after 400 years.}

\bverse And also the nation whom they serve I will judge; afterward they shall come out with great possessions.
\bverse Now as for you, you shall go to your fathers in peace; you shall be buried at a good old age.
\bverse But in the fourth generation they shall return here, for the iniquity of the \people{Amorites} \textit{is} not yet complete.''
\bverse And it came to pass, when the sun went down and it was dark, that behold, there appeared a smoking oven and a burning torch that passed between those pieces.
\bverse On the same day the \lord made a covenant with \name{Abram}, saying:
\bverse ``To your descendants I have given this land, from the river of \Egypt to the great river, the \location{River of Euphrates}--
\bverse the \people{Kenites}, the \people{Kenezzites}, the \people{Kadmonites},
\bverse the \people{Hittites}, the \people{Perizzites}, the \people{Raphaim}, the \people{Amorites}, the \people{Canaanites}, the \people{Girgashites}, and the \people{Jebusites}.''
